### 2021-08-02 paper-acm.tex
Initial commit

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,10pt]{acmart}

\settopmatter{printfolios=true}

\usepackage{hyperref}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{A Unified Interaction Model For Web Scraping \& Customization}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Kapaya Katongo}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{kkatongo@mit.edu}

\author{Geoffrey Litt}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{glitt@mit.edu}

\author{Kathryn Jin}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{kjin@mit.edu}

\author{Daniel Jackson}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{dnj@csail.mit.edu}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Web scraping, the process of extracting structured data from a
  website, is a common building block of web customization systems.
  Prior approaches have allowed users to perform web scraping by
  directly demonstrating examples of the data to scrape. However,
  demonstrations alone do not allow for as much expressiveness as
  traditional programming which is vital for complex web scraping tasks.

  In this paper, we present a new interaction model for web scraping
  that combines the ease of use of programming-by-demonstration and the
  expressiveness of traditional programming. When a user demonstrates
  examples of data to extract, a web scraping program is synthesized and
  presented in a formula language with pure functional semantics.
  Crucially, the user can directly edit and execute formulas, allowing
  them to express scraping operations which can not be achieved via
  demonstration alone.

  To illustrate our model, we implement it as a browser extension called
  Joker. Through concrete examples, a small user study and a Cognitive
  Dimenions of Notation analysis, we show how Joker offers an expressive
  interaction model for web scraping and customization.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{end-user programming, software customization, web scraping, programming-by-example, program synthesis}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\hypertarget{sec:introduction}{%
\section{Introduction}\label{sec:introduction}}

Many websites on the internet do not meet the exact needs of all of
their users. Because of this, millions of people use browser extensions
like Greasemonkey \citep{zotero-224} and Tampermoneky \citep{2021f} to
install userscripts, snippets of Javascript code which customize the
behavior of websites. To make the creation of web customizations more
accessible to end-users without knowledge of programming, researchers
have developed systems like Sifter \citep{huynh2006}, Vegemite
\citep{lin2009} and Wildcard \citep{litt2020, litt2020b}.

A common building block of these web customization systems is web
scraping, the extraction of structured data from websites. They achieve
web scraping in one of two ways: programming-by-demonstration
\citep{huynh2006, lin2009} and traditional programming
\citep{litt2020, litt2020b}. Web scraping by demonstration automates the
web scraping process by utilizing program synthesis to synthesize a web
scraping program from user demonstrations. This approach is accessible
to end-users with no programming experience and enables them to fully
participate in the customization lifecycle. However, web scraping by
demonstration is not powerful enough to perform certain complex web
scraping tasks. On the other side, web scraping by programming involves
programmers manually writing web scraping code. It is powerful enough to
scrape a wider variety of websites but is not accessible to end-users
who can only customize websites that programmers have written web
scraping code for.

In this paper, we present a new interaction model for web scraping for
customization that combines the ease of use of
programming-by-demonstration and the expressiveness of traditional
programming. At its core lies a simple formula language. The language
offers pure functional semantics for expressing and executing data
extractions from websites using Cascading Style Sheet (CSS) selectors.
When a user demonstrates examples of data to scrape, a web scraping
program is synthesized via wrapper induction \citep{kushmerick2000} and
is presented as a formula containing the CSS selector required to
identify the Document Object Model (DOM) element with the data
(Section~\ref{sec:implementation}). Crucially, the formula can be
directly edited and executed to specify complex scraping operations
which can not be achieved by demonstrations alone.

To illustrate our new interaction model for web scraping, we have
implemented it as an extension of Wildcard \citep{litt2020, litt2020b}
called Joker. Wildcard is a browser extension that enables web
customization by direct manipulation of a spreadsheet-like table it adds
to websites. The table contains the website's underlying structured data
and is bidirectionally synchronized with it. User interactions with the
table, including sorting, adding columns and running computations in a
spreadsheet formula language, are propagated to the website thereby
customizing it. The web scraping required to create Wildcard's table can
only be achieved via traditional programming in Javascript. This means
that end-users can only customize websites that programmers have written
web scraping code for. Joker enables end-users to achieve the web
scraping tasks required for customization while maintaining some of the
expressiveness of traditional programming.

By representing web scraping programs as formulas, our web scraping
interaction model fit right into Wildcard's customization paradigm which
utilizes formulas for web customization. This enabled us to go beyond
providing an interaction model that combines web scraping by
demonstration with web scraping by programming to providing an
interaction model that combines web scraping \emph{and} customization.
We refer to this as a \emph{unified interaction model for web scraping
and customization}. In Section~\ref{sec:examples}, we show how this
offers more expressive web scraping and customization.

Our contributions are as follows:

\begin{itemize}
\tightlist
\item
  A \textbf{unified interaction model for web scraping and
  customization} that combines web scraping (by demonstration and
  programing) with web customization through a shared formula language
  with pure functional semantics
\item
  An implementation of the unified interaction model for web scraping
  and customization called Joker that combines three key design
  principles (\textbf{prodirect manipulation}, \textbf{functional
  reactive programming} \& \textbf{unified user interaction}) in a novel
  way (Section~\ref{sec:design-principles})
\item
  The results of an evaluation of the model via an example gallery, a
  five person user study and a Cognitive Dimensions of Notion analysis
  (Section~\ref{sec:evaluation})
\end{itemize}

We end by discussing opportunities for future work and how we can make
CSS selectors more accessible to end-users without development
experience (Section~\ref{sec:conclusion}).

\hypertarget{sec:examples}{%
\section{Example Usage Scenario}\label{sec:examples}}

To concretely illustrate the user experience of our tool, we present a
scenario of customizing eBay, a popular online marketplace. The goal of
the user, Jen, is to filter out search results that are sponsored,
i.e.~product listings that a seller paid to promote. On the webpage,
sponsored listings are marked with a ``Sponsored'' label that Jen can
try to scrape, then she can sort the scraped labels to move all
sponsored listings to the bottom of the page. Figure~\ref{fig:ebay}
shows accompanying screenshots.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/ebay.png}
  \caption{\label{fig:ebay}Scraping and customizing eBay by unified demonstration and formulas.}
\end{figure*}

\emph{Scraping Names by Demonstration} (Figure~\ref{fig:ebay} Part A):
Jen starts the adapter creation process by clicking a context menu item
within the eBay.com page, then hovering over the data that she would
like to scrape: the page element that contains the name of the listing.
The system provides live feedback as Jen hovers: it annotates the row of
data with a border, highlights the column of data in the page with a
green background, and displays how the values will appear in the data
table. When she clicks, the highlighted data is saved into the table.

The text content of the highlighted element is now displayed in the
first column of the table, with one cell for each listing containing the
name of the listing. When she clicks on a cell, Jen can see that the
textual data is also represented by a formula:

\texttt{QuerySelector(rowElement,\ "h3.s-item\_\_title")}

This formula reveals how Joker is actually scraping this column's data
behind the scenes: it calls a query selector on each listing (i.e.~each
\texttt{rowElement}) on the page. Scraped data is stored as functions
that act on the data on the page, instead of as static text, based on
our design principle of \textbf{functional reactive programming}. Joker
exposes this formula to the user to exemplify how scraping is achieved
with formulas and to provide a template for scraping with formulas.

After this first demonstration, Jen has a reference to each of the
page's row elements (i.e.~each product listing) in the Joker table. She
can now use these references to scrape elements within the product
listing with formulas, such as the Sponsored label.

\emph{Scraping Sponsored Labels with Formulas} (Figure~\ref{fig:ebay}
Part B): Next, Jen attempts to scrape contents of the ``Sponsored''
label element into a new column; having this column would allow her to
sort the table based on whether the listing contains the ``Sponsored''
label. She tries to scrape the label using demonstration, but she is
unable to scrape more than one letter of the word at a time. To diagnose
the issue, Jen inspects the page's source code using her browser's
developer tools. Jen discovers that eBay's developers have inserted
invisible letters into word ``Sponsored'' (possibly to obfuscate against
ad blockers). Each letter is in its own HTML element, and the inserted
letters are rendered invisible by CSS. Scraping by demonstration does
not work in this case because Jen wants the element that contains the
whole word, but the system is giving her the leaf-node elements
(individual letters) instead.

Jen sees in the source code that the all of the letters of the
``Sponsored'' label, both visible and invisible, are contained in a
single ancestor element with the CSS selector
\texttt{"div.s-item\_\_title-\/-tagblock"}. Thus, she is able to scrape
the full word by writing a query selector formula with with that CSS
selector. She can copy the formula from the previous column as a
template.

This formula populates the column with the text content of the
``Sponsored'' element, which she can now use for string manipulation and
sorting. By writing a formula, Jen is able to overcome the limitations
of scraping by demonstration. The mixed methods of scraping exemplify
our tool's support of \textbf{prodirect manipulation}.

\emph{Filtering Sponsored Results} (Figure~\ref{fig:ebay} Part C): The
query selector that Jen just wrote returns all of the text within each
of the targeted ``Sponsored'' elements, including any invisible letters.
eBay's web design is that sponsored listings have a visible
``Sponsored'' label with invisible inserted letters, and non-sponsored
listings have an invisible ``Sponsored'' label. Thus, for sponsored
listings, the query returns garbled text
(e.g.~``JSp3onMsoV3rXNYFedZB''), and for non-sponsored listings, the
query returns ``Sponsored.'' Jen identifies this correlation by
scrolling through the scraped data in the column and comparing them to
what she sees on the web page. Then, in a new column, Jen writes a
formula that returns whether or not the previous column's text includes
the word ``Sponsored.'' Finally, she sorts the listings by whether or
not they are sponsored by sorting this column, thus hiding sponsored
results from view. This customization is possible because Joker provides
a \textbf{unified user model}, where scraping and customization are
performed in conjunction.

In this way, Jen is able to use our system to customize the eBay
website, without needing to learn how to program in JavaScript and
without even leaving the webpage. Our model of customization by unified
demonstration and formulas is flexible enough to support a wide range of
other useful modifications and web programming proficiency levels, and
we present a greater variety of use cases in
Section~\ref{sec:evaluation}.

\hypertarget{sec:implementation}{%
\section{System Implementation}\label{sec:implementation}}

In this section, we outline the \emph{wrapper induction}
\citep{kushmerick2000} algorithm that Joker uses to synthesize web
scraping programs from user demonstrations. Then, we briefly describe
the formula language used to represent the synthesized web scraping
programs and include a list of the formulas that are currently available
and their roles.

\hypertarget{wrapper-induction}{%
\subsection{Wrapper Induction}\label{wrapper-induction}}

In order to create web scraping programs from users demonstrations,
Joker solves the wrapper induction \citep{kushmerick2000} task:
generalizing from a few examples of data in a data set to a
specification for all the data in the data set.

Joker takes an approach similar to that used in systems like Vegemite
\citep{lin2009} and Sifter \citep{huynh2006}. It synthesizes a single
\emph{row selector} for the website: a CSS selector that identifies a
set of DOM elements corresponding to the rows of the data set. For each
column in the data set, it synthesizes a \emph{column selector}, a CSS
selector that identifies the element containing the column value.

One important difference is that our algorithm only accepts row elements
that have direct siblings with a similar structure. We refer to this as
the \emph{row-sibling} constraint. Later, we describe how this
constraint provides a useful simplification of the wrapper induction
task and in \citep{section:evaluation} discuss the resulting limitations
this puts on our system. We proceed to describe how CSS selectors are
synthesized for row and column elements and then explain the criteria
used to determine row elements.

\hypertarget{synthesizing-css-selectors}{%
\subsubsection{Synthesizing CSS
Selectors}\label{synthesizing-css-selectors}}

Joker synthesizes two types of CSS selectors: a single row selector that
selects a set of DOM elements corresponding to the rows of the data set
and a column selector for each column which selects the element
containing the column value within a given row.

For a given row element, its row selector is synthesized using the
following criteria:

\emph{Plausibility}. A selector is set of classes. It is a plausible row
selector if it 1) consists of a subset of the classes on the row element
and 2) consists of a subset of the classes all the row element's
siblings. The second requirement is the \emph{row-sibling} constraint we
mentioned. Notice how it simplifies the problem by eliminating
selectors. It is necessary for the end goal of customization because of
customizations like sorting. If row elements are not siblings, the
website would end up in an invalid state when the DOM elements are
re-organized to match the sorting order.

\emph{Weight}. A selector has a weight equal to the number of classes it
consists of.

\emph{Best}. A selector is the best if it is plausible and there is no
other selector that has a lower weight than it. We favor selectors with
the lowest weight to ensure that only the minimum required classes are
utilized. If there are multiple selectors that are plausible and have
the lowest weight, we only pick one.

For a given column element, its column selector is synthesized using the
following criteria:

\emph{Plausibility}. A selector is a plausible column selector if it 1)
consists of a subset of the classes on the column element and 2) only
selects the give column element when applied on the corresponding row
element.

\emph{Weight}. A selector has a weight equal to the number of classes it
consists of.

\emph{Best}. A selector is the best if it is plausible and there is no
other selector that has a lower weight than it has. As before, we favor
selectors with the lowest weight and only pick one if there are multiple
that fulfill the criteria.

One aspect of future work is saving the list of all selectors that
fulfill the criteria and making them available to users to view and pick
from via the formula. This would be similar to Mayer et el's user
interaction model called \emph{program navigation} \citep{mayer2015}
that gives users the opportunity to navigate all valid, synthesized
programs and pick the best one.

\hypertarget{determining-row-elements}{%
\subsubsection{Determining Row
Elements}\label{determining-row-elements}}

When a user first demonstrates a column value, Joker uses the
demonstration to synthesize a row selector. The row selector will be
used to identify all the row elements in the website. Additionally, a
column selector is synthesized that will be used to identify the element
that contains the column value. During subsequent demonstrations, Joker
simply synthesizes a column selector for the column element that
contains the demonstrated column value. Like similar approaches
\citep{huynh2006, lin2009, chasins2018}, all demonstrations have to be
made from the same row element.

Given a demonstrated column value, row elements are determined using the
following criteria:

\emph{Plausibility}. An element \texttt{R} is a plausible row element if
1) it is within the \texttt{BODY} element of the DOM, 2) it is in the
parent path of the column element \texttt{C} containing the demonstrated
column value \texttt{V} and 3) the CSS selector \texttt{S} of element
\texttt{C} identifies a column element \texttt{C\textquotesingle{}} when
applied to \texttt{R}

\emph{Weight}. A row element \texttt{R} has a weight \texttt{W} equal to
the number of its siblings for which the CSS selector \texttt{S} of
column element \texttt{C} only identifies \texttt{C} when applied to it.
This is an enforcement of the \emph{row-sibling} constraint. We want to
find an \texttt{R} with the most number of siblings with a similar
structure

\emph{Best}. A row element \texttt{R} is the best if it is plausible and
there is no other row element that has a higher weight than it. We favor
row elements with the highest weight to ensure that we end up with a
data set with the highest number of column values corresponding to the
column that \texttt{V} belongs to. If there are multiple plausible row
elements with the highest weight, we pick the one closet to the column
element \texttt{C} in its parent path.

Figure~\ref{fig:algorithm} provides a concrete example of how the above
criteria are applied to determine a row element from the demonstration
of a column value.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/algorithm.png}
  \caption{\label{fig:algorithm} An example of how Joker's wrapper indunction algorithm is used to determine the row element from the demonstration of a column value. The row element is correctly determind to be R2 because it is plausible and has the highest weight.}
\end{figure*}

\hypertarget{web-scraping-formulas}{%
\subsection{Web Scraping Formulas}\label{web-scraping-formulas}}

Joker's formula language is similar to that of visual database query
systems like SIEUFERD \citep{bakke2016} and Airtable \citep{2021f}.
Formulas automatically apply across an entire column of data and
reference other column names instead of values in specific rows. This is
more efficient than users having to copy a formula across a column as in
traditional spreadsheets like Microsoft Excel and Google Sheets. It of
course comes at the cost of not being able to specify a formula for only
a subset of column cells but this hasn't yet come up in our use cases.
The language currently consists of the following formulas:

\hypertarget{queryselectorrowelement-selector}{%
\subsubsection{QuerySelector(rowElement,
selector)}\label{queryselectorrowelement-selector}}

This formula is used to represent the web scraping program synthesized
from demonstrations. \texttt{rowElement} is a special keyword that
references a hidden column containing the DOM elements that correspond
to the rows of the data set. \texttt{selector} is the synthesized CSS
selector that specifies the column element.

\hypertarget{getparentelement}{%
\subsubsection{GetParent(element)}\label{getparentelement}}

This formula is used to traverse the DOM when the data to be scraped is
made of the values of its containing and sibling elements.
Demonstrations alone cannot be used to scrape such data.
\texttt{element} can be a reference to a column containing a
\texttt{QuerySelector} formula (\texttt{GetParent(A)}) or a
\texttt{QuerySelector} formula itself
(\texttt{=GetParent(QuerySelector(...))}).

\hypertarget{getattributeelement-attribute}{%
\subsubsection{GetAttribute(element,
attribute)}\label{getattributeelement-attribute}}

This formula is used to scrape data from DOM attributes. An example of
this are URLs which are available on the \texttt{href} attribute of link
elements. \texttt{element} is as described for \texttt{GetParent} and
\texttt{attribute} is the name of the attribute to scrape
(e.g.~\texttt{GetAttribute(A,\ "href")}).

\hypertarget{sec:design-principles}{%
\section{Design Principles}\label{sec:design-principles}}

Below, we describe three design principles that Joker embodies. We did
not invent these principles but rather combined them in a novel manner
for the domain of web scraping and web customization.

\hypertarget{prodirect-manipulation}{%
\subsection{Prodirect Manipulation}\label{prodirect-manipulation}}

\emph{Prodirect Manipulation} is a term coined by Ravi Chugh in a
position paper \citep{chugh2016a} in which he advocates for ``novel
software systems that tightly couple programmatic and direct
manipulation.'' This principles embodies our goal of an interaction
model for web scraping that combines the ease of use of
programming-by-demonstration and the expressiveness of traditional
programming.

In the eBay example in Section~\ref{sec:examples}, we show how the
``Sponsored'' label of a listing can not be scraped by demonstration
alone. However, through Joker's prodirect manipulation interaction, a
user can either directly edit the synthesized web scraping formula or
author one from scratch to achieve the task. This is significant because
the resulting customization to sort the listings by whether they are
sponsored or not would not otherwise be possible

We can see prodirect manipulation in other programming-by-example
systems. Sketch-N-Sketch \citep{chugh2016} allows users to create an SVG
shape via traditional programming and then switch to modifying its size
or shape via direct manipulation. Wrex \citep{drosos2020} takes examples
of data transforms and generates readable and editable Python code.

\hypertarget{functional-reactive-programming}{%
\subsection{Functional Reactive
Programming}\label{functional-reactive-programming}}

Functional reactive programming (FRP) utilizes pure functions to specify
operations in a reactive programming paradigm. FRP has seen wide
adoption in end-user programming through implementations such as
spreadsheet formula languages (Microsoft Excel \& Google Sheets) and
formula languages for low-code programming environments (Microsoft Power
Fx \citep{2021g}, Google AppSheet \citep{2021h}, Airtable \citep{2021f},
Glide \citep{2021a}, Coda \citep{2021c} \& Gneiss \citep{chang2014}).

Joker's use of FRP makes it easier for users to specify scraping
operations programmatically, thus making our web scraping interaction
model more viable. With traditional programming, the eBay example in
Section~\ref{sec:examples} in which demonstrations are not enough to
scrape a listing's ``Sponsored'' label would be much more complicated.
The user would need to understand programming constructs such as state,
variables, looping and data flow in order to write a program to scrape
the label. In Joker, all a user needs to specify is the CSS selector
that identifies the element containing the label. Joker takes care of
managing state, variables, looping and data flow!

A key limitation of this approach is that users need to understand how
CSS selectors work. Because the formula language utilizes pure
functional semantics, users can iterate on CSS selectors as many times
as they need to without having to worry about side effects. This makes
the authoring of CSS selectors more accessible but more work remains for
us to make this fully accessible to end-users.

\hypertarget{unified-user-interaction}{%
\subsection{Unified User Interaction}\label{unified-user-interaction}}

Prior to this work, web scraping and web customization in customization
systems \citep{huynh2006, lin2009} were divided: web scraping had to be
performed prior to customization in a separate phase. Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
findings from its user study in which participants thought that ``it was
confusing to use one technique to create the initial table, and another
technique to add information to a new column.''

Joker represents web scraping and customization using the same formula
language. Because of this, both can be performed in a single phase, with
users being able to interleave the two as desired. This makes the
process of customization more incremental which is vital for complex
tasks. We can see this in the Ebay example in
Section~\ref{sec:examples}: when the user scrapes a listing's
``Sponsored'' label, they observe that non-sponsored listings have an
invisible ``Sponsored'' label while sponsored listings have a visible
``Sponsored'' label that consists of a garbled form ``Sponsored.''
Because of Joker's unified user interaction, the user receives the
results of scraping in the table and can immediately write a
customization formula to validate this hypothesis. Without the unified
interaction, the user would have to scrape all the desired columns to
see all their values before ever getting to notice the pattern and
validate their hypothesis.

\hypertarget{sec:evaluation}{%
\section{Evaluation}\label{sec:evaluation}}

In this section, we evaluate Joker with an example gallery of websites,
a small user study and a Cognitive Dimensions of Notion analysis
\citep{blackwell2001}. The example gallery provides examples of websites
that can be scraped and customized by Joker and known limitations. The
user study provides insights on which aspects of Joker work well and
which don't. The Cognitive Dimensions of Notion analysis provides
thoughts on how Joker's design compares to similar approaches and
interaction standards.

\hypertarget{example-gallery}{%
\subsection{Example Gallery}\label{example-gallery}}

Following a method used to evaluate visualizations through a diverse
gallery of examples \citep{ren2018}, our first evaluation of Joker
provides an example gallery of popular websites on which Joker can be
used for web customization and on which it can not be used. For the
websites on which Joker can be used, we provide the sequence of
interactions needed to achieve the customizations. For the websites on
which Joker cannot be used, we provide an explanation.

\hypertarget{websites-joker-can-be-used-on}{%
\subsubsection{Websites Joker Can Be Used
On}\label{websites-joker-can-be-used-on}}

We have used Joker to achieve a variety of purposes across many popular
websites. For example, we have used Joker to sort search results by
price within the Featured page on Amazon. (Using Amazon's sort by price
feature often returns irrelevant results.) In Amazon's source code, the
price is split into three HTML elements: the dollar sign, the dollar
amount, and the cents amount. A user can only scrape the cents element
by demonstration into column A. However, because the parent element of
the cents element contains all three of the price elements, the user can
scrape the full price using the formula \texttt{GetParent(A)}. Next, the
user can write the formula \texttt{ExtractNumber(B)} to convert the
string into a numeric value. Finally, the user can sort this column by
low-to-high prices. In a similar manner, we have used Joker to scrape
and sort prices and ratings on the product listing pages of Target and
eBay.

We have also found Joker to be useful for filtering based on text
inputs. For example, we have used Joker to filter the titles of a
researcher's publications on their Google Scholar profile. Specifically,
a user can first scrape the titles into column A by demonstration. Then,
the user can write the formula \texttt{Includes(A,\ "compiler")} that
returns whether or not the title contains the keyword ``compiler.''
Finally, the user can sort by this column to get all of the publications
that fit their constraint at the top of the page. We have also used
Joker to filter other text-based directory web pages such as Google
search results and the MIT course catalog, in similar ways.

Additionally, we have used Joker to augment web pages with external
information. For example, Joker can augment Reddit's old user interface,
which has a list of headlines with links to articles and images. A user
can first scrape the headline elements into column A by demonstration.
The user can then extract the link into column B with the formula
\texttt{GetAttribute(A,\ "href")}. Then, the user can write the formula
\texttt{ReadTimeInSeconds(B)} that calls an API that returns the links'
read times. Similarly, the user can write the formula
\texttt{Visited(B)} that returns whether that link has been visited in
the user's browser history. The user can also scrape elements such as
the number of comments and the time of posting and sort by these values.
We have performed similar customizations on websites such as ABC news.

\hypertarget{limitations}{%
\subsubsection{Limitations}\label{limitations}}

Joker's unified model of demonstrations and formulas is most effective
on webpages with data that is presented as many similarly-structured
HTML elements. However, certain websites have designs that make it
difficult for Joker to scrape data. These are some of those designs:

\begin{itemize}
\tightlist
\item
  \emph{Multiple row elements.} The layout of some web pages has
  multiple types of row as siblings that contain different children
  elements. For example, the news aggregator website HackerNews has a
  page design that alternates between rows containing a title and rows
  containing supplementary data (e.g.~number of likes and the time of
  posting). Because Joker only chooses a single row selector, when
  scraping by demonstration, Joker will only select one of the types of
  rows, and elements in the other types of rows will not be able to be
  scraped.
\item
  \emph{Infinite scroll.} Some web pages have an ``infinite scroll''
  feature that adds new entries to the page when a user scrolls to the
  bottom. Joker's table will only contain elements that were rendered
  when the table was first created. Additionally, for websites with many
  elements, such as Facebook, Joker might run out of memory while
  running its wrapper induction algorithm and crash the page.
\item
  \emph{Data hidden behind an interaction.} On some sites, a user must
  click on an element to reveal data corresponding to that entry
  (e.g.~time of posting, the author). However, Joker is restricted to
  scraping what is visible on the page at one point in time.
\end{itemize}

\hypertarget{user-study}{%
\subsection{User Study}\label{user-study}}

Our second evaluation of Joker is a user study which provides insights
on what aspects of Joker work well and what don't. Because of this,
successful completion of tasks does not equal validation of Joker. It
does however inform us about usability issues that limit its
effectiveness.

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We recruited 5 participants with backgrounds ranging from limited
programming experience to Software Engineers. All participants were
familiar with Microsoft Excel spreadsheets but not all had used Excel
spreadsheet formulas. 4 of the participants had web development
experience with 3 of them having extensive experience. 3 of the
participants had web scraping experience with only 1 having extensive
experience.

\hypertarget{tasks}{%
\subsubsection{Tasks}\label{tasks}}

The participants completed 7 tasks across 2 websites towards the goal of
web customization. The first website was MIT's course catalog and the
second was a listing of iPhones after searching for ``iPhone'' on eBay.
The tasks were as follows:

\emph{MIT Course Catalog.} This set of tasks involved web scraping by
demonstration and the use of web customization formulas: 1a) Scrape
course titles, 1b) Scrapes course prerequisites, 1c) Add a column that
indicates whether a course has a prerequisite \& 1d) Add a column that
indicates whether a course does not have a prerequisite and is offered
in the fall.

\emph{eBay.} This set of tasks involved web scraping by demonstration,
the use of web scraping formulas and the use of web customization
formulas: 2a) Scrape iPhone listing title, 2b) Scrape iPhone listing
price, \& 2c) Create a column that indicates whether an iPhone listing
is sponsored.

\hypertarget{protocol}{%
\subsubsection{Protocol}\label{protocol}}

All participants attempted the MIT course catalog and eBay tasks in the
order we have described. We started each session with a description of
Joker and provided a brief tutorial of its main features on a website
not used for the tasks. There was no time limit for tasks but we
provided hints whenever a participant had exhausted the knowledge
available to them.

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

All participants were able to complete all the tasks with the help of
hints when they got stuck and were unable to make progress on their own.
Again, this does not equal validation. We describe the results along the
following dimensions:

\emph{Web Scraping By Demonstration.} All participants where able to
complete the tasks that only involved scraping by demonstration (1a, 1b
\& 2a) quickly and without any hints. For tasks that involved switching
between demonstrations and writing formulas, there was some confusion
about what column demonstrated values would be scraped into. The active
column is managed by a toolbar at the top of the website but
participants hardly noticed it and assumed all operations had to be
performed on the table.

\emph{Web Scraping Formulas.} Participants were unsure why
demonstrations did not work when completing tasks that required using
web scraping formulas (2b, 2c). As a result, they wasted time attempting
to demonstrate using various means. The participant with no web
development experience had the hardest time as expected but was able to
utilize a series of hints we provided to accomplish 2b. The rest of the
participants were able to accomplish 2b with minimal hints but required
a lot more when completing 2c.

\emph{Web Customization Formulas.} Participants had varying degrees of
trouble when completing the tasks that involved using web customization
formulas (1c, 1d, 2c). Most of the confusion resulted from formula
parameters and return values. The formula bar has an autocomplete
feature that shows the documentation for a given formula. The
documentation consists of the parameters a formula it takes and a brief
description of each parameter. However, this wasn't always sufficient to
enable participants to use formulas correctly.

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

One participant, upon seeing our tutorial on scraping by demonstration,
said ``that's like black magic.'' Tasks that involved customization
formulas took longer than those that involved demonstrations but this
was mostly related to the formula documentation not providing enough
usage information. More work is needed to show users what exactly a
given formula does. When asked how they would accomplish the tasks
without Joker, the participant with limited programming experience
responded with ``I don't think I would know how to do it.'' That Joker
enabled them to achieve such a complex task is very promising!

Participants that were familiar with web development were able to take
advantage of Joker's web scraping formulas. This included the
participants that had limited web scraping experience and suggests that
the pure functional semantics and use of CSS selectors for identifying
elements to scrape makes the task easier. As predicted, participants not
familiar with web development didn't have the required background to
understand how CSS selectors work. This highlights the need to further
explore how web scraping formulas can be made more accessible to
end-users.

All participants had trouble figuring out which column the demonstrated
values would be scraped into, especially when demonstrations where
interleaved with use of formulas. This points to the need for the switch
between demonstrating and using formulas to be more tightly coupled
visually. For web scraping formulas, the most notable issue was the lack
of feedback about why demonstrations were not sufficient to scrape a
value. As a result, users wasted time trying to demonstrate in various
ways instead of thinking about using web scraping formulas to achieve
the task. In order for traditional programming to augment demonstrations
as we propose, users need to recieve some kind of feedback that
demonstrations are not sufficient.

\hypertarget{cognitive-dimensions-analysis}{%
\subsection{Cognitive Dimensions
Analysis}\label{cognitive-dimensions-analysis}}

Our third evaluation of Joker analyzes it using Cognitive Dimensions of
Notation \citep{blackwell2001}, a heuristic evaluation framework that
has been used to evaluate programming languages and visual programming
systems \citep{satyanarayan2014, satyanarayan2014a, ledo2018}. When
contrasting our tool with traditional scraping and other visual tools,
we find particularly meaningful differences along several of the
dimensions:

\emph{Progressive evaluation.} In Joker, a user can see the intermediate
results of their scraping and customization work at any point, and
adjust their future actions accordingly. The table user interface makes
it easy to inspect the intermediate results and notice surprises like
missing values.

In contrast, traditional scraping typically requires editing the code,
manually re-running it, and inspecting the results in an unstructured
textual format, making it harder to progressively evaluate the results.
Also, many end-user scraping tools \citep{chasins2018, lin2009} require
the user to demonstrate all the data extractions they want to perform
before showing any information about how those demonstrations will
generalize across multiple examples.\footnote{This is an instance where
  Joker's limitation of only scraping a single page at a time proves
  beneficial. All the relevant data is already available on the page
  without further network requests, making it possible to support
  progressive evaluation with low latency. Other tools that support
  scraping across multiple pages necessarily require a slower feedback
  loop.}

\emph{Premature commitment.} Many scraping tools require making a
\emph{premature commitment} to a data schema: first, the user extracts a
dataset, and then they perform downstream analysis or customization
using that data. Wildcard suffered from this problem: when writing code
for a scraping adapter, a user would need to try to anticipate all
future customizations and extract the necessary data.

Our current system instead supports extracting data \emph{on demand}.
The user can decide on their desired customizations and data
transformations, and extract data as needed to fulfill those tasks.
There is never a need to eagerly guess what data will be needed in
advance.

We have also borrowed a technique from spreadsheets for avoiding
premature commitment: default naming. New data columns are automatically
assigned a single-letter name, so that the user does not need to
prematurely think of a name before extracting the data. We have not yet
implemented the capability to optionally rename demonstrated columns,
but it would be straightforward to do so, and would provide a way to
offer the benefits of names without requiring a premature commitment.

\emph{Provisionality.} Joker makes it easy to try out a scraping action
without fully committing to it. When the user hovers over any element in
the page, they see a preview of how that data would be entered into the
table, and then they can click if they'd like to proceed. This makes it
feel very fast and lightweight to try scraping different elements on the
page.

\emph{Viscosity.} Some scraping tools have high viscosity: they make it
difficult to change a single part of a scraping specification without
modifying the global structure. For example, in Rousillon
\citep{chasins2018}, changing the desired demonstration for a single
column of a table requires re-demonstrating all of the columns. In
contrast, Joker allows a user to change the specification for a single
column of a table without modifying the others, resulting in a lower
viscosity in response to changes.

\emph{Role-expressiveness.} One dimension we are still exploring in our
tool is role-expressiveness: having different elements of a program
clearly indicate their role to the user. In particular, in our current
design, the visual display of references to DOM elements in the table is
similar to the display of primitive values. In our experience, this can
sometimes make it difficult to understand which parts of the table are
directly interacting with the website, vs.~processing the downstream
results. In the future we could consider adding more visual
differentiation to help users understand the role of different parts of
their customization.

\hypertarget{sec:related-work}{%
\section{Related Work}\label{sec:related-work}}

Joker builds on existing work in end-user web scraping, end-user web
customization and program synthesis by a number of systems.

\hypertarget{end-user-web-scraping}{%
\subsection{End-user Web Scraping}\label{end-user-web-scraping}}

FlashExtract \citep{le2014} is a programming-by-example tool for data
extraction. In addition to demonstrating whole values, it supports
demonstrating substrings of values. Joker only supports this through
formulas. This is not as end-user friendly but allows for a wider range
of operations such as indicating whether demonstrated values contain a
certain value or are greater than or less than a certain value.

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. It presents the web scraping program
generated by demonstration as an editable, high-level, block-based
language called Helena \citep{2021c}. While Helena can be used to
specify complex web scraping tasks like adding control flow, it does not
present the synthesized web scraping program. This means that users can
only scrape what can be demonstrated. Joker on the other hand displays
the synthesized program as a formula which can be modified to increase
the expressiveness of scraping.

\hypertarget{end-user-web-customization}{%
\subsection{End-user Web
Customization}\label{end-user-web-customization}}

Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
Unlike Joker, its table interface is only populated and can only be
interacted with after all the demonstrations have been provided. This
does not support interleaving of scraping and table operations to
achieve an incremental workflow for users. Mashups are created using
CoScripter \citep{leshed2008} which records operations on the scraped
values in the table for automation tasks. CoScripter provides the
generated automation program as text-based commands, such as ``paste
address into `Walk Score' input,'' which can be edited via ``sloppy
programming'' \citep{lin2009} techniques. However, this editing does not
extend to the synthesized web scraping program which is not displayed
and therefore cannot be modified. This means that users can only scrape
what can be demonstrated.

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. It attempts to automatically detect
items and fields on the page with a variety of clever heuristics. If
this falls, it gives the user the option of demonstrating to correct the
result. In contrast, Joker is simpler and makes fewer assumptions about
the structure of websites by giving control to the user from the
beginning of the process and displaying the synthesized program which
can be modified. We hypothesize that focusing on a tight feedback loop
rather than automation may support a scraping process that is just as
fast as an automated one, offers more expressive scraping and extends to
a greater variety of websites. However, further user user testing is
required to validate this hypothesis.

\hypertarget{program-synthesis}{%
\subsection{Program Synthesis}\label{program-synthesis}}

FlashProg \citep{mayer2015} is a framework that provides program
navigation and disambiguation for programming-by-example tools like
FlashExtract \citep{le2014} and FlashFill \citep{harris}. The program
viewer provides a high level description of synthesized programs as well
as a way to navigate the list of alternative programs that satisfy the
demonstrations. This is important because demonstrations are an
ambiguous specification for program synthesis \citep{peleg2018}: the set
of synthesized programs for a demonstration can be very large. To
further ensure that the best synthesized program is arrived at,
FlashProg has a disambiguation viewer that asks the user questions in
order to resolve ambiguities in the user's demonstrations. In contrast,
Joker only presents the top-ranked synthesized program which may not be
the best one. Furthermore, the program is presented in is low-level form
as a CSS selector. This is not end-user friendly but allows for more
expressiveness.

\hypertarget{sec:conclusion}{%
\section{Conclusion And Future Work}\label{sec:conclusion}}

In this paper, we presented our unified interaction model for web
scraping and customization through a browser extension called Joker.
This model combines the ease of use of programming-by-demonstration and
the expressiveness of traditional programming. At its core lies a simple
formula language that offers pure functional semantics for expressing
and executing data extractions from websites using Cascading Style Sheet
(CSS) selectors.

The main area of future work involves providing feedback to users about
when demonstrations are not sufficient. Otherwise, users won't know to
switch to formulas to take advantage of their increased expressiveness.
FlashProg \citep{mayer2015} and Wrangler \citep{kandel2011}, whose
interfaces also have tables, offer clues for how to provide feedback
about the execution of programs synthesized from demonstrations. Another
important area involves making the formula language more accessible to
end-users not familiar with CSS selectors. Again, FlashProg offers some
clues through its use of high level descriptions to give meaning to
synthesized programs. One avenue for associating meaning with CSS
selectors could be by extracting semantic web content as seen in systems
like Thresher \citep{hogue2005}.

% \printbibliography

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references-bibtex.bib}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2021-08-02 paper.tex
Initial commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[sort, numbers]{natbib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Make font size smaller in bibliography, as per:
% https://tex.stackexchange.com/questions/386709/proper-usage-of-biblatex-ieee-biblatex-style-in-an-ieeetran-document
\renewcommand*{\bibfont}{\footnotesize}

% begin pandoc tex stuff

\usepackage{hyperref}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% end pandoc tex stuff

\begin{document}

\title{Joker: A Unified Interaction Model For Web Customization}

% removing authors for anonymous submission

% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}}

\maketitle

\begin{abstract}
Tools that enable end-users to customize websites typically use a
two-stage workflow: first, users extract data into a structured form;
second, they use that extracted data to augment the original website in
some way. This two-stage workflow poses a usability barrier because it
requires users to make upfront decisions about what data to extract,
rather than allowing them to incrementally extract data as they augment
it.

In this paper, we present a new, unified interaction model for web
customization that encompasses both extraction and augmentation. The key
idea is to provide users with a spreadsheet-like formula language that
can be used for both data extraction and augmentation. We also provide a
programming-by-demonstration (PBD) interface that allows users to create
data extraction formulas by clicking on elements in the website. This
model allows users to naturally and iteratively move between extraction
and augmentation.

To illustrate our unified interaction model, we have implemented a tool
called Joker which is an extension of Wildcard, a prior web
customization system. Through case studies, we show that Joker can be
used to customize many real-world websites. We also present a formative
user study with five participants, which showed that people with a wide
range of technical backgrounds can use Joker to customize websites, and
also revealed some interesting limitations of our approach. Finally, we
present a heuristic evaluation of our design using the Cognitive
Dimensions framework.
\end{abstract}

\begin{IEEEkeywords}
end-user web customization, programming-by-demonstration, spreadsheets, end-user web scraping, program synthesis
\end{IEEEkeywords}

\hypertarget{sec:introduction}{%
\section{Introduction}\label{sec:introduction}}

Many websites do not meet the exact needs of all of their users, so
millions of people use browser extensions and userscripts
\citep{zotero-224, 2021f} to customize them. However, these tools only
allow end-users to install customizations built by programmers. End-user
web customization systems like Sifter \citep{huynh2006}, Vegemite
\citep{lin2009} and Wildcard \citep{litt2020} provide a more accessible
approach, allowing anyone to create bespoke customizations without
performing traditional programming.

These tools each provide different useful mechanisms for end-user
customization, but they share a common design limitation: they have a
rigid separation between the two stages of the web customization
process. First, in the \emph{extraction} or \emph{scraping} phase, users
get data from the website into a structured, tabular format. Second, in
the \emph{augmentation} phase, users perform augmentations like adding
new columns derived from the data, or sorting the data. For example, in
Vegemite, a user can extract a list of addresses from a housing catalog,
and then augment the data by computing a walkability score for each
address.

This separation between extraction and augmentation poses an important
barrier to usability. A user study \citep{lin2009} of Vegemite wrote
that ``it was confusing to use one technique to create the initial
table, and another technique to add information to a new column.'' The
creators of Sifter similarly reported \citep{huynh2006} that ``the
necessity for extracting data before augmentation could take place was
poorly understood, if understood at all.'' In Wildcard, end-users cannot
augment a website at all until a programmer has written and shared
extraction code for that website in Javascript \citep{litt2020}. These
tools all impose a sequential workflow in which users must first extract
all the data they need, and then perform all their desired
augmentations. This workflow exemplifies the more general problem in
interface design of forcing users to make premature commitments to
formal structure \citep{shipman1999, blackwell2001}.

In this paper, we present a new approach to web customization that
combines extraction and augmentation in a unified interaction model. Our
key idea is to develop a domain specific language (DSL) that encompasses
both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to program in the language. This unified interaction model
allows end-users to move seamlessly between extraction and augmentation,
resulting in a more iterative and free-form workflow for web
customization.

To demonstrate and evaluate this model, we have built a browser
extension called Joker, an extension of the Wildcard customization tool.
The original Wildcard system \citep{litt2020} adds a spreadsheet-like
table to a website and establishes a bidirectional synchronization
between the website and the table. This allows users to customize a
website, by filtering and sorting page elements, and adding user
annotations, derived values and calls to web services. Although Wildcard
offers a declarative formula language for augmenting the page, a
conventional imperative language (namely JavaScript) is used for the
extraction step, and the extraction code cannot be modified during
augmentation.

Joker makes two primary contributions:

\textbf{A unified formula language for extraction \& augmentation}:
Wildcard's formula language only supported primitive values like strings
and numbers aimed at augmentation. Joker extends this language by
introducing Document Object Model (DOM) elements as a new type of value,
and adding a new set of formulas for performing operations on them. This
includes querying elements with Cascading Style Sheets (CSS) selectors
and traversing the DOM. With this approach, a single formula language is
used to express both extraction and augmentation tasks, even within a
single formula expression.

\textbf{A PBD interface for creating extraction formulas}: Directly
writing extraction formulas can be challenging for end-users, so Joker
provides a PBD interface that synthesizes formulas from user
demonstrations. A key aspect of our design is that the program
synthesized from the demonstration is made visible as a spreadsheet
formula that can be subsequently edited by the user, and is more easily
understood than imperative code due to its declarative form.

Section~\ref{sec:examples} describes a concrete scenario, showing how
Joker enables a user to complete a useful customization task. In
Section~\ref{sec:implementation}, we outline the implementation of our
formula language and user interface, as well as the algorithms used by
our PBD interface.

We have performed three evaluations of our approach, presented in
Section~\ref{sec:evaluation}. First, we describe a suite of case studies
in which we used Joker to extract and augment a variety of websites in
order to characterize its capabilities and limitations. Second, we
describe a formative user study with five participants, which showed
that users were generally able to use Joker to perform useful extraction
and augmentation tasks, but which also uncovered limitations,
particularly for less experienced users trying to extract data from more
complex websites. Finally, we perform a heuristic evaluation of our
design, using the Cognitive Dimensions \citep{blackwell2001} framework.

Joker relates to existing work not only in end-user web customization,
but also in end-user web scraping and program synthesis, which we
discuss in Section~\ref{sec:related-work}. Finally, we discuss
opportunities for future work in Section~\ref{sec:conclusion}.

\hypertarget{sec:examples}{%
\section{Example Usage Scenario}\label{sec:examples}}

Here is an example scenario, illustrated in Figure~\ref{fig:ebay}, and
demonstrated in the video accompanying this paper. Jen is searching for
a karaoke machine on eBay, a shopping website. She wants to use Joker to
sort products by price within a page of search results, a feature not
supported by eBay.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/ebay.png}
  \caption{\label{fig:ebay}Scraping and customizing eBay by unified demonstration and formulas.}
\end{figure*}

\emph{Extracting Product Titles \& Prices By Demonstration}.
(Figure~\ref{fig:ebay} Part A): Jen initiates Joker through the browser
context menu. As she hovers over the product title, Joker provides two
kinds of live feedback. First, it highlights the titles of all the
corresponding product listings on the page, to indicate how it has
generalized Jen's intent based on her demonstration of a single example
product. Second, a column of the table is populated with the values that
will be extracted, giving a preview of how the extracted data would
look. To commit to this extraction, Jen clicks on the product title. She
repeats a similar process to extract the price.

When she clicks one of the cells in column \texttt{B}, the formula bar
above the table displays the extraction formula that was generated from
her demonstration:

\texttt{=QuerySelector(rowElement,\ "span.s-item\_\_price")}

This formula produces the values in column \texttt{B}. For each row in
the table, Joker has a created a reference to the corresponding DOM
element, accessible through the special identifier \texttt{rowElement}.
The \texttt{QuerySelector} function runs the specified CSS selector
(\texttt{span.s-item\_\_price}) within the row element to extract the
price of each item. While Jen could directly edit this formula, in this
case the values in the table are correct, so there's no need to edit the
formula.

\emph{Sorting Products By Price}. (Figure~\ref{fig:ebay} Part B): Next,
Jen wants to sort the table by price, but she realizes that the column
of prices is a list of strings containing the \texttt{\$} symbol. She
needs to \emph{augment} this raw data by turning the strings into
numbers. In the next column (\texttt{C}), Jen starts typing a formula,
and uses an autocomplete dropdown to find a relevant function that
extracts numeric values from strings:

\texttt{=ExtractNumber(B)}

Now column C contains numeric values, so Jen can sort the table by
price. Because the table is synchronized with the website, the product
listings become sorted as well.

\emph{Extracting Product URL With Formulas} (Figure~\ref{fig:ebay} Part
C): While completing the previous task, Jen realizes there is another
customization she would find useful: prioritizing products for which she
has not yet visited the details page for the listing. To do this, she
must first return to \emph{extracting} more relevant data from the page.

Each product listing links to a page for the specific product, but
because the URL is not visible in the page, it's not possible to
directly extract it by demonstration. However, Jen can still achieve the
goal by directly writing an extraction formula.

Jen has some basic knowledge of HTML, which she can leverage to write
the formula. She opens the browser developer tools, and observes that
the listing title is represented by a link tag with a heading inside:

\begin{verbatim}
<a href="LISTING PAGE URL">
  <h3>LISTING NAME</h3>
</a>
\end{verbatim}

Since there is already a column \texttt{A} in the table representing the
product's title, she can use this as a starting point to write the
formula:

\texttt{=GetAttribute(GetParent(A),\ "href")}

This formula first calls the \texttt{GetParent} function on column
\texttt{A}, traversing up a level from the
\texttt{\textless{}h3\textgreater{}} elements to the
\texttt{\textless{}a\textgreater{}} elements. Then,
\texttt{GetAttribute} extracts the \texttt{href} value containing the
link URL. After running this formula, the table contains a column
\texttt{D} with the URL for each product.

\emph{Sorting Products By Whether They Have Been Visited}
(Figure~\ref{fig:ebay} Part C): After performing that extraction, Jen
can write a final augmentation formula to indicate whether she has
visited the corresponding product page:

\texttt{=Visited(D)}

The \texttt{Visited} function checks whether a URL is present in the
browser history and returns a boolean value represented by a checkbox.
Jen can then sort by this column to put listings that she has not yet
visited at the top of the page.

Using Joker, Jen was able to not only achieve her initial customization
goal to sort the products by price but also perform a customization she
did not plan to do. This was made possible by Joker's unified
interaction model for web customization which enabled her to interleave
extraction and augmentation. While we have described only a single
illustrative scenario in this example, Joker is flexible enough to
support a wide range of other useful customizations and workflows on
various websites, described in more detail in
Section~\ref{sec:evaluation}.

\hypertarget{sec:implementation}{%
\section{System Implementation}\label{sec:implementation}}

\begin{figure*}
  \includegraphics[width=\textwidth]{media/overview.png}
  \caption{\label{fig:overview}An overview of Joker's interaction model and wrapper induction process.}
\end{figure*}

In this section, we describe Joker's formula language in more detail.
Then, we outline the \emph{wrapper induction} \citep{kushmerick2000}
algorithm that Joker's PBD interface uses to synthesize the row element
and column selectors presented in formulas. Figure~\ref{fig:overview}
illustrates the entire process.

\hypertarget{extraction-formulas}{%
\subsection{Extraction Formulas}\label{extraction-formulas}}

The Wildcard customization tool includes a formula language for
augmentation, including operators for basic arithmetic and string
manipulation, as well as more advanced operators that fetch data from
web APIs. As in other tabular interfaces like SIEUFERD \citep{bakke2016}
and Airtable \citep{2021f}, formulas apply to a whole column at a time
rather than a single cell, and can reference other columns by name.
Joker extends this base language with new constructs which enable it to
apply to \emph{data extraction} instead of just augmentation.

We added DOM elements as a data type in the language, alongside strings,
numbers, and booleans. Because the language runs in a JavaScript
interpreter, we simply use native JavaScript values to represent DOM
elements in the language. DOM elements are displayed visually by showing
their inner text contents. They can also be implicitly typecast to
strings for use in other formulas; for example, a string manipulation
formula like \texttt{Substring} can be called on a DOM element value,
and will operate on its text contents.

We also added several functions to the formula language for traversing
the DOM and performing extractions, summarized below with their types:

\begin{itemize}
\tightlist
\item
  \texttt{QuerySelector(el:\ Element,\ sel:\ string):\ Element}.
  Executes the CSS selector \texttt{sel} inside of element \texttt{el},
  and returns the first matching element.
\item
  \texttt{GetAttribute(el:\ Element,\ attribute:\ string):\ string}.
  Returns the value for an attribute on an element.
\item
  \texttt{GetParent(el:\ Element):\ Element}. Returns the parent of a
  given element.
\end{itemize}

To extract data from a row, formulas need a way to reference the current
row, so we added a construct to support this use case. Every row in the
table maps to one DOM element in the page; we allow formulas to access
this DOM element via a special keyword, \texttt{rowElement}. In some
sense, \texttt{rowElement} can be seen as a hidden extra column of data
in the table containing DOM elements.

While many more functions could be added to expose more of the
underlying DOM API, we found that in practice these three functions
provided ample power through composition. For example, in
Section~\ref{sec:examples} we showed how \texttt{GetParent} and
\texttt{GetAttribute} can be composed to traverse the DOM and extract
the URL associated with a product listing.

By providing a single formula language to express extractions and
augmentations, Joker enables a \emph{unified interaction model} that
supports interleaving the two. Furthermore, the formula language enables
users to specify logic using pure, stateless functions that reactively
update in response to upstream changes. This \emph{functional reactive
paradigm} is easier to reason about than traditional imperative
programming, as demonstrated by the use of formulas by millions of end
users in spreadsheet programs and end-user programming environments
\citep{2021g, 2021h, 2021f, 2021a, 2021c, chang2014}.

\hypertarget{wrapper-induction}{%
\subsection{Wrapper Induction}\label{wrapper-induction}}

When users demonstrate a specific column value to extract, Joker must
synthesize a program that reflects the user's general intent. This is an
instance of the \emph{wrapper induction} problem of synthesizing a web
data extraction query from examples. Prior work on this topic
\citep{kushmerick2000, furche2016} prioritizes accuracy and robustness
to future changes, which makes sense for a fully automated system, but
can lead to very complex queries. In our work, we chose to prioritize
the readability of queries by less sophisticated users, so that users
can more easily author queries and repair them when they break. We
implemented a set of heuristics inspired by Vegemite \citep{lin2009} for
wrapper induction, described below.

\hypertarget{determining-row-elements}{%
\subsubsection{Determining Row
Elements}\label{determining-row-elements}}

The user starts by demonstrating an element \(v\), representing a value
that should be in the table. From that demonstration, we must find a set
of \emph{row elements} that represent the rows of the table. We could
naively assume that \(parent(v)\) is the row containing \(v\), but often
\(v\) is deeply nested inside its containing row; we must determine
which ancestor of \(v\) is likely to be the row.

Intuitively, we solve this problem by assuming that all rows share some
similar internal structure. In particular, we expect most rows to
contain a value for the demonstrated column. (If there were no missing
data, we'd expect \emph{all} rows to contain data for this column.)

Formally: assume a function \(select(el, s)\) which runs a CSS selector
that returns the set of elements matching \(s\) within \(el\). We
generate a set of plausible candidates \(P\), consisting of pairs of a
row element and a CSS selector:

\(P = \{ (r, s) \mid r \in ancestors(v) \land select(r, s) = \{v\} \}\)

For each candidate \((r, s) \in P\), we compute a weight function \(w\),
which is based on the number of siblings of \(r\) that have ``similar
structure'', defined by checking whether running \(s\) within the
sibling also returns a unique element.

\(w(r, s) = |\{ r' \mid r' \in siblings(r) \land |select(r', s) | = 1 \}|\)

We then choose the candidate with the highest weight. In case of ties,
the candidate closer to \(v\) in the tree (i.e., lower in the tree)
wins. Given a winning candidate \((r, s)\), the full set of row elements
is \(\{r\} \cup siblings(r)\).

\hypertarget{synthesizing-css-selectors-for-column-values}{%
\subsubsection{Synthesizing CSS Selectors For Column
Values}\label{synthesizing-css-selectors-for-column-values}}

Once we have determined the row elements, next we must choose a CSS
selector that will be used to identify the demonstrated value within its
row.

Given a demonstrated value \(v\) within a row element \(r\), we generate
two kinds of plausible selectors:

\begin{itemize}
\tightlist
\item
  selectors using CSS classes, which are manual annotations on DOM
  elements added by the website's programmers, typically for styling
  purposes (e.g.~"item\_\_price")
\item
  selectors using positional indexes within the tree, using the
  \texttt{nth-child} CSS selector (e.g.~\texttt{nth-child(2)},
  representing the second child of an element)
\end{itemize}

The minimum criteria for a plausible selector \(s\) is that it uniquely
identifies the value within the row: \(select(r, s) = \{v\}\). But there
may be many plausible selectors, so we must pick a best one.

We first prioritize selectors using classes, because they tend to be
more robust to changes on the website. A single selector can combine
multiple classes, but we prefer using fewer classes when possible. If no
plausible class-based selector can be generated (for example, if the
relevant elements don't have any classes to query), we fall back to
using a positional index selector. This kind of selector can always be
generated regardless of the contents of the page, but tends to be less
accurate and robust.

\hypertarget{sec:evaluation}{%
\section{Evaluation}\label{sec:evaluation}}

We evaluate our interaction model and tool in terms of three research
questions:

\emph{RQ1: What kinds of websites can this model operate effectively
on?} We evaluate this with a suite of case studies that demonstrate its
capabilities and limitations.

\emph{RQ2: How are users of different backgrounds able to use the
system?} We evaluate this with a small formative user study.

\emph{RQ3: What are the essential design dimensions that distinguish
this model from other approaches?} We evaluate this with a heuristic
analysis using the Cognitive Dimensions of Notation framework
\citep{blackwell2001}.

\hypertarget{case-studies}{%
\subsection{Case Studies}\label{case-studies}}

Our first evaluation describes the results of the authors using Joker to
extract data and perform customizations on popular websites. For the
websites on which Joker can be used, we provide the sequence of
interactions needed to achieve the customizations; for the websites on
which Joker fails, we explain the relevant limitations.

\hypertarget{successful-applications}{%
\subsubsection{Successful Applications}\label{successful-applications}}

\begin{table*}[]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Website}              & \textbf{Example Customization Achieved by Joker}                                        \\ \hline
eBay, Amazon            & Filter listings by whether they have a "Sponsored" label.                        \\
Amazon, Target & Sort search results by price and rating.                                                \\
Google Scholar                & Filter publications for those whose title contains a user-provided keyword. \\
Reddit, CNN, ABC  & Sort by the read times of articles. Filter already-visited articles.         \\
Weather.com                   & Filter hourly weather to find sunny times of day.                                        \\
Github                        & Sort a user's code repositories by stars to find popular work.                          \\
Postmates, Uber Eats    & Sort restaurants by delivery time and delivery fee.                                     \\ \hline
\end{tabular}
\vspace{8pt}
\caption{Examples of websites that Joker can be used to customize, including extraction and augmentation}
\end{table*}

We have used Joker to achieve a variety of customizations across many
websites. Table 1 summarizes examples we have found on popular websites.

\emph{Sorting search results by price on Amazon.} We have found Joker to
be useful for sorting the contents of various websites. One example of a
useful sort achieved by Joker is sorting search results by price within
the Featured page on Amazon. (Using Amazon's sort by price feature often
returns irrelevant results.) In Amazon's source code, the price is split
into three HTML elements: the dollar sign, the dollar amount, and the
cents amount. A user can extract by demonstration only the cents element
into column \texttt{A}. Subsequently, because the parent element of the
cents element contains all three of the price elements, the user can
extract the full price using the formula \texttt{GetParent(A)}. Next,
the user can write the formula \texttt{ExtractNumber(B)} to convert the
string into a numeric value. Finally, the user can sort this column by
low-to-high prices. In a similar manner, we have used Joker to extract
and sort prices and ratings on the product listing pages of Target and
eBay.

\emph{Filtering titles of publications on Google Scholar.} We have also
found Joker can be useful for filtering a website's listings based on
the text content of an element in the listing. For example, we have used
Joker to filter the titles of a researcher's publications on their
Google Scholar profile which is not natively supported. First, a user
can extract the titles into a column (\texttt{A}) by demonstration.
Then, the user can write the formula \texttt{Includes(A,\ "compiler")}
that returns whether or not the title contains the keyword ``compiler''.
Finally, the user can sort by this column to get all of the publications
that fit their constraint at the top of the page. We have also used
Joker to filter other text-based directory web pages such as Google
search results and the MIT course catalog, in similar ways.

\emph{Retrieving information about links on Reddit.} Additionally, we
have used Joker to augment web pages with external information. For
example, Joker can augment Reddit's user interface, which has a list of
headlines with links to articles, with the links' read times and whether
the link has already been read. To achieve this customization, a user
first extracts the headline elements into column (\texttt{A}) by
demonstration. The user can then extract the link into the next column
(\texttt{B}) with the formula \texttt{GetAttribute(A,\ "href")}. Then,
the user can write the formula \texttt{ReadTimeInSeconds(B)} that calls
an API that returns the links' read times. Similarly, the user can write
the formula \texttt{Visited(B)}, which uses another API that returns
whether that link has been visited in the user's browser history. The
user can also extract elements such as the number of comments and the
time of posting and sort by these values. We have performed similar
customizations on websites such as ABC News and CNN.

\hypertarget{limitations}{%
\subsubsection{Limitations}\label{limitations}}

Joker is most effective on websites whose data is presented as a
collection of similarly-structured HTML elements. Certain websites,
however, have designs that make it difficult for Joker to extract data:

\begin{itemize}
\tightlist
\item
  \emph{Heterogeneous row elements.} Some websites break their content
  into rows, but the rows do not have a consistent layout, and contain
  different types of child elements. For example, the page design of
  HackerNews alternates between rows containing a title and rows
  containing supplementary data (e.g.~number of likes and the time of
  posting). Because Joker only chooses a single row selector, when
  extracting by demonstration, Joker will only select one of the types
  of rows, and elements in the other types of rows will not be
  extracted.
\item
  \emph{Infinite scroll.} Some websites have an ``infinite scroll''
  feature that adds new entries to the page when a user scrolls to the
  bottom. Joker's table will only contain elements that were rendered
  when the table was first created. Additionally, for websites that
  render a very large number of DOM elements, the speed of the live
  feedback provided by Joker's PBD interface might significantly
  decrease. This is because the wrapper induction process used by the
  PBD interface queries the DOM which takes longer as the size of the
  DOM increases.
\end{itemize}

\hypertarget{user-study}{%
\subsection{User Study}\label{user-study}}

We conducted a small formative user study to understand how people would
interact with Joker.

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We recruited 5 participants with varying backgrounds. 3 participants
were familiar with spreadsheet formulas. 3 participants had extensive
web development experience, 1 had a small amount of prior web
development experience, and 1 had no web development experience. 3
participants had previously extracted data from websites.

\hypertarget{protocol}{%
\subsubsection{Protocol}\label{protocol}}

The participants completed 7 web customization tasks across 2 websites.
All participants attempted all the tasks.

First, we asked participants to customize a website with a relatively
simple HTML structure: the MIT EECS course catalog website. All data
\emph{extraction} on this site can be performed with demonstrations
alone in Joker, although augmentation still requires writing formulas.
The specific tasks were the following: 1a) Extract course titles, 1b)
Extract course prerequisites, 1c) Add a column that indicates whether a
course has a prerequisite \& 1d) Add a column that indicates whether a
course has no prerequisites and is offered in the fall term.

Next, we asked participants to customize a website with a more complex
HTML structure: the search results page for the eBay shopping website.
Due to the website's complexity, demonstrations alone are not sufficient
to extract data; users must also directly edit extraction formulas. The
specific tasks were the following: 2a) Extract title from listings of
Apple iPhones for sale, 2b) Extract the listing price for the phone, \&
2c) Create a column that indicates whether a listing for a phone is
sponsored.

Each session was 60 minutes long and conducted over a recorded video
conference. We started each session with a description of Joker and
provided a brief tutorial of its main features on a sample website not
used in the tasks. There was no time limit for completing the tasks.
Users were encouraged to speak aloud as they worked.

Because some of the tasks build on results of previous tasks, we wanted
to ensure all participants made enough progress to gather useful
feedback. Therefore, whenever a participant got stuck for several
minutes, we recorded why they were stuck and then offered hints on how
to proceed (such as suggestions to read formula documentation or open
the browser dev tools). While all participants were able to complete all
tasks with hints, this obviously does not mean they could have completed
the task unassisted. Our goal was not to simply measure whether users
completed the task, but rather to gain qualitative insight into the
barriers they faced.

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

\emph{Unified interaction model.} Most participants took advantage of
the unified interaction model to interleave extraction and augmentation
tasks, rather than performing all extraction up front. For example, on
task 1, most participants extracted the prerequisites by demonstration,
added one or more columns to the table to perform some string operations
on the prerequisites, and then continued on to extract more information
from the web page by demonstration. Furthermore, we hypothesize that in
a less controlled setting, users would be even more likely to interleave
extraction and augmentation, since the task may be less well defined at
the beginning.

One usability issue with the unified model was that participants
sometimes got confused about how their demonstrations would affect the
contents of the table. For example, multiple participants intended to
add a new column by demonstrating an extraction, but instead
accidentally overwrote the contents of an existing column. This poses a
design challenge because the user's demonstrations occur in the website,
so they cannot directly interact with the table while demonstrating;
this suggests that the interface needs to do a better job indicating
where the results of a demonstration will be inserted.

\emph{Extracting simple data.} On the relatively simple MIT course
catalog website, all participants were able to extract the relevant data
from the page within seconds, simply performing demonstrations with a
few clicks. This suggests that when Joker's generalization algorithm
works well, it can be an effective tool for data extraction, even for
users with limited programming experience. P1 said: \emph{``you could
hover and {[}the data{]} was already selected\ldots that was very
nice''}. P3, upon seeing the tutorial for extraction by demonstration,
said \emph{``that's like black magic.''}

\emph{Extracting complex data.} On the more complex eBay website where
demonstration alone was not sufficient, results were more varied. P1,
who had no prior web development experience, struggled to complete the
task, saying that \emph{``looking at HTML is a bit much''}; this
suggests that more work could be done to make the experience usable for
novices. However, users with more web development experience were able
to use the tool to perform complex extractions, such as directly writing
CSS selectors into the formula bar. P2 and P3 both reported that Joker's
live feedback loop was easier to use and faster than other approaches to
web extraction; P3 noted that \emph{``{[}with any other approach{]}, it
would have been slower to specify and slower to validate that I
specified it correctly.''}

It was challenging for some participants to switch between using the
browser's developer tools and the Joker interface when doing complex
extraction tasks. While we chose not to build HTML inspection into the
Joker UI because the browser already provides a very rich set of tools,
users sometimes were not able to tell how elements in the Joker table
corresponded to elements in the browser's element inspector.

\emph{Writing formulas.} In general, participants were able to learn the
formula language by using an autocomplete dropdown with inline
documentation, which we developed as part of the Joker extension. In
some cases, participants were able to immediately construct correct
formulas on the first try; in other cases it took several attempts and
some hints from the moderator to try a relevant function. While better
documentation and error messages could help improve the learnability of
the formula language, we also did not find it surprising that
participants required some time to learn a completely unfamiliar formula
language.

\hypertarget{cognitive-dimensions-analysis}{%
\subsection{Cognitive Dimensions
Analysis}\label{cognitive-dimensions-analysis}}

We analyzed Joker using the Cognitive Dimensions of Notation
\citep{blackwell2001}, a heuristic evaluation framework that has been
used to evaluate programming languages and visual programming systems
\citep{satyanarayan2014, satyanarayan2014a, ledo2018}. When contrasting
our tool with other scraping and customization tools, we find
particularly meaningful differences along several dimensions:

\emph{Progressive evaluation.} In Joker, a user can see the intermediate
results of their extraction and augmentation work at any point, and
adjust their future actions accordingly. The table user interface makes
it easy to inspect the intermediate results and notice surprises like
missing values.

In contrast, traditional extraction typically requires editing the code,
manually re-running it, and inspecting the results in an unstructured
textual format, making it harder to progressively evaluate the results.
Also, many end-user extraction tools \citep{chasins2018, lin2009}
require the user to demonstrate all the data extractions they want to
perform before showing any information about how those demonstrations
will generalize across multiple examples.\footnote{This is an instance
  where Joker's limitation of only scraping a single page at a time
  proves beneficial. All the relevant data is already available on the
  page without further network requests, making it possible to support
  progressive evaluation with low latency. Other tools that support
  scraping across multiple pages necessarily require a slower feedback
  loop.}

\emph{Premature commitment.} Many scraping tools require making a
\emph{premature commitment} to a data schema: first, the user extracts a
dataset, and then they perform augmentations using that data. Wildcard
suffered from this problem: when writing code for extraction, a user
would need to anticipate all future augmentations and extract the
necessary data.

Joker instead supports extracting data \emph{on demand}. The user can
decide on their desired augmentations and extract data as needed to
fulfill those tasks. There is never a need to eagerly guess what data
will be needed in advance.

We have also borrowed a technique from spreadsheets for avoiding
premature commitment: default naming. New data columns are automatically
assigned a single-letter name, so that the user does not need to
prematurely think of a name before extracting the data. We have not yet
implemented the capability to optionally rename demonstrated columns,
but it would be straightforward to do so, and would provide a way to
offer the benefits of names without requiring a premature commitment.

\emph{Provisionality.} Joker makes it easy to try out an extraction
action without fully committing to it. When the user hovers over any
element in a website, they see a preview of how that data would be
extracted into the table, and then they can click if they'd like to
proceed. This makes it feel very fast and lightweight to try scraping
different elements on the page.

\emph{Viscosity.} Some scraping tools have high viscosity: they make it
difficult to change a single part of an extraction specification without
modifying the global structure. For example, in Rousillon
\citep{chasins2018}, changing the desired demonstration for a single
column of a table requires re-demonstrating all of the columns. In
contrast, Joker allows a user to change the specification for a single
column of a table without modifying the others, resulting in a lower
viscosity in response to changes.

\hypertarget{sec:related-work}{%
\section{Related Work}\label{sec:related-work}}

Joker builds on existing work in end-user web customization, end-user
web scraping and program synthesis.

\hypertarget{end-user-web-customization}{%
\subsection{End-user Web
Customization}\label{end-user-web-customization}}

Joker builds on web customization ideas implemented by previous tools.
Our contribution is a new interaction model that allows for interleaving
extraction and augmentation, enabled by a unified formula language and a
PBD interface.

Joker is an extension of the Wildcard customization system
\citep{litt2020}, and preserves its foundational idea of synchronizing a
table with a website. Wildcard only allows for extraction logic to be
written by programmers in Javascript; our work has substantially
extended the Wildcard formula language and added an entire new system
for dynamically creating data extraction logic within the user
interface. We also improved the formula editing interface by adding an
autocomplete dropdown and documentation popup, which proved important in
our testing for allowing end-users to reliably edit and create formulas.

Vegemite \citep{lin2009} is a tool for end-user programming of web
mashups. Like Joker, it allows users to perform demonstrations to
extract data, but Vegemite only displays a table after all the
demonstrations have been provided, which rules out interleaving
extraction and augmentation. Vegemite does allow users to directly view
and edit some of the logic generalized from demonstrations, but it only
allows for editing augmentation logic, not extraction logic. The wrapper
induction algorithm used in Joker is also very similar to Vegemite's
algorithm.

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. It attempts to automatically detect
items and fields on the website with a variety of heuristics. If these
fail, it gives the user the option of demonstrating to correct some
parts of the result. In contrast, Joker makes fewer assumptions about
the structure of websites, by giving control to the user from the
beginning of the process and displaying an editable synthesized program.
We hypothesize that focusing on a tight feedback loop rather than
automation may support a scraping process that offers more expressive
power and extends to a greater variety of websites, but further user
testing is required to validate this hypothesis. Of course, better
heuristics could benefit our model as well; the ideal system would make
good guesses while giving the user full understanding and control of the
extraction process.

\hypertarget{end-user-web-scraping-and-program-synthesis}{%
\subsection{End-user Web Scraping and Program
Synthesis}\label{end-user-web-scraping-and-program-synthesis}}

Joker builds on insights from other tools that synthesize web scraping
(i.e.~data extraction) code from user demonstrations, and give users
ways to inspect and modify the generated code.

Rousillon \citep{chasins2018} is a tool that enables end-users to
extract hierarchical web data across multiple linked web pages. It
presents the web extraction program generated from demonstrations in an
editable, high-level, block-based language called Helena \citep{2021c}.
While both Rousillon and Joker create an editable program, they have
different focuses. Because Rousillon allows users to extract data across
multiple pages (e.g., extracting details from each linked page in a
list), it uses an imperative language, with nested loops as a key
construct. In contrast, Joker can only extract within a single page, and
therefore can use a simpler declarative formula language. Also,
Rousillon only allows editing high-level control flow and treats some
details of the extraction logic as opaque; Joker offers finer-grained
control over details like CSS selectors.

Mayer et al propose a user interaction model called \emph{Program
Navigation} \citep{mayer2015} which aims to give users another mechanism
beside examples for guiding the generalization process of PBE tools like
FlashExtract \citep{le2014} and FlashFill \citep{harris}. This is
important because demonstrations are an ambiguous specification for
program synthesis \citep{peleg2018}: the set of synthesized programs for
a demonstration can be very large. The Program Navigation UI displays a
natural language description of a space of possible programs, and lets
the user choose different alternatives for parts of the generated
expression. Joker shares the general idea of displaying synthesized
programs, but only presents the top-ranked program; our tool might be
improved by showing more candidate programs.

More broadly, Joker's use of PBD to generate editable code embodies Ravi
Chugh's notion of \emph{prodirect manipulation} \citep{chugh2016a},
which aims to bridge the divide between programmatic and direct
manipulation. The Sketch-N-Sketch system \citep{chugh2016} provides
prodirect manipulation by allowing users to create an SVG shape via
traditional programming and then switch to modifying its size or shape
via direct manipulation.

\hypertarget{sec:conclusion}{%
\section{Conclusion And Future Work}\label{sec:conclusion}}

In this paper, we presented a unified interaction model for web
customization. Our key idea is a spreadsheet formula language that
encompasses both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to program to create formulas. This unified interaction model
allows end-users to move seamlessly between extraction and augmentation,
resulting in a more iterative and free-form workflow for web
customization.

The main area of future work involves making the formula language more
accessible to end-users not familiar with CSS selectors. FlashProg
offers some clues through its use of natural language descriptions to
explain synthesized extraction programs. One avenue for explaining CSS
selectors could be by extracting semantic web content associated with
the elements they select, as seen in systems like Thresher
\citep{hogue2005}.

Our ultimate goal is to enable anyone that uses the web to customize
websites in the course of their daily use in an intuitive and flexible
way. This will in turn make the malleability of the web a reality for
all of its users.

\newpage

\bibliographystyle{IEEEtran}
\bibliography{references-bibtex.bib}

\end{document}

### 2021-08-02 templates/programming-template/example-programming.tex
Initial commit

% -*- coding: utf-8; -*-
% vim: set fileencoding=utf-8 :
\documentclass[english,submission]{programming}
%% First parameter: the language is 'english'.
%% Second parameter: use 'submission' for initial submission, remove it for camera-ready (see 5.1)

\usepackage[backend=biber]{biblatex}
\addbibresource{example.bib}

%
% Packages and Commands specific to article (see 3)
%
% These ones  are used in the guide, replace with your own.
%
\usepackage{multicol}
\lstdefinelanguage[programming]{TeX}[AlLaTeX]{TeX}{%
  deletetexcs={title,author,bibliography},%
  deletekeywords={tabular},
  morekeywords={abstract},%
  moretexcs={chapter},%
  moretexcs=[2]{title,author,subtitle,keywords,maketitle,titlerunning,authorinfo,affiliation,authorrunning,paperdetails,acks,email},
  moretexcs=[3]{addbibresource,printbibliography,bibliography},%
}%
\lstset{%
  language={[programming]TeX},%
  keywordstyle=\firamedium,
  stringstyle=\color{RosyBrown},%
  texcsstyle=*{\color{Purple}\mdseries},%
  texcsstyle=*[2]{\color{Blue1}},%
  texcsstyle=*[3]{\color{ForestGreen}},%
  commentstyle={\color{FireBrick}},%
  escapechar=`,}
\newcommand*{\CTAN}[1]{\href{http://ctan.org/tex-archive/#1}{\nolinkurl{CTAN:#1}}}
%%

\begin{document}

\title{The Art, Science, and Engineering of Programming}
\subtitle{Preparing Articles for Programming}% optional
\titlerunning{Preparing Articles for Programming} %optional, in case that the title is too long; the running title should fit into the top page column

\author[a]{Tobias Pape}
\authorinfo{is the author of this {LaTeX} class. Contact him at
  \email{tobias.pape@hpi.uni-potsdam.de}.}
\affiliation[a]{Hasso Plattner Institute, University of Potsdam, Germany}
\author{Cristina V. Lopes}
\authorinfo{is associate editor for the first two issues of The Art, Science,
  and Engineering of Programming. Contact her at \email{lopes@ics.uci.edu}.}
\affiliation{University of California, Irvine, USA}
\author[a]{Robert Hirschfeld}
\authorinfo{is chair of the AOSA steering committee. The Art, Science,
  and Engineering of Programming is published by AOSA. Contact Robert at \email{hirschfeld@hpi.uni-potsdam.de}.}

% \authorrunning{T. Pape, C. Lopes, R. Hirschfeld} % Optional, for long author lists

\keywords{programming journal, paper formatting, submission preparation} % please provide 1--5 keywords

%%%%%%%%%%%%%%%%%%
%% These data MUST be filled for your submission. (see 5.3)
\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=art,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Social Coding, General-purpose programming},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by,
}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% These data are provided by the editors. May be left out on submission.
%\paperdetails{
%  submitted=2016-08-10,
%  published=2016-10-11,
%  year=2016,
%  volume=1,
%  issue=1,
%  articlenumber=1,
%}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10003459</concept_id>
<concept_desc>General and reference~Computing standards, RFCs and guidelines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010476.10010477</concept_id>
<concept_desc>Applied computing~Publishing</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{General and reference~Computing standards, RFCs and guidelines}
\ccsdesc[500]{Applied computing~Publishing}

% To HERE
%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

% Please always include the abstract.
% The abstract MUST be written according to the directives stated in
% http://programming-journal.org/submission/
% Failure to adhere to the abstract directives may result in the paper
% being returned to the authors.
\begin{abstract}
  Many academic journals and conferences exist that publish
  research related to programming, starting with programming languages,
  software engineering, and expanding to the whole Computer Science field. Yet,
  many of us feel that, as the field of Computer Science expanded, programming,
  in itself, has been neglected to a secondary role not worthy of scholarly
  attention.

  We posit that a scholarly journal focusing primarily on programming
  will help close this gap, and foster a more meaningful bridge
  between research and the practice of software development.

  The Art, Science, and Engineering of Programming accepts papers
  under several perspectives: the art itself (programming styles,
  pearls, models, languages), the emerging science of understanding what works
  and what doesn’t work in general and in specific contexts, as well as more
  established engineering and mathematical perspectives.

  This journal aims at placing the wonderful art of programming in the
  map of scholarly works.

  We present this short paper as an example of, and a guide to,
  writing articles for The Art, Science, and Engineering of
  Programming journal. The complete template is provided: the class
  file (\texttt{programming.cls}), an example paper (\texttt{example-programming.tex}, this file), and an example
  bibliography file (\texttt{example.bib}).

  Much of the progress in Computer Science lies on the basis of
  computer programs, the people who write them, and the concepts and
  tools available to them to express computational tasks. The
  existence of a journal focusing on programming is of utmost
  importance for strengthening our understanding of these activities.
\end{abstract}

\section{A Guided Tour}
\label{sec:guided-tour}

The content of a paper is its most important ingredient. That being said,
papers for The Art, Science, and Engineering of Programming should adhere to a
common style, which is achieved with the \lstinline|programming| {LaTeX}
class. You are to use this class as outlined here when submitting articles to
the journal. This document acts as an example of what this can look like and a
short references for all its parts.

\subsection{Document Parts}
\label{sec:document-parts}

\begin{lstlisting}[float,label=lst:tour,caption={A very minimal article.}]
\documentclass[english,submission]{programming}`\label{l:doc}`
\usepackage[backend=biber]{biblatex} % Use Biblatex `\label{l:bib}`
\addbibresource{example.bib}

\begin{document}

\paperdetails{`\label{l:details}`
  perspective=engineering,
  area={General-purpose programming}
}

\title{The importance of why and how to do work}`\label{l:meta}`
\author{Anna Author}
\affiliation{The Unseen University, Ankh-Morpork}
\author{Bert Betatester}
\affiliation{Carolingian Minuschool Academy, Bodoni, San Serriffe}

\keywords{paper, showcase, lorem ipsum}`\label{l:keywords}`

\begin{CCSXML}`\label{l:ccs:start}`
<ccs2012>
<concept>
<concept_id>10002944.10011122.10003459</concept_id>
<concept_desc>General and reference~Computing standards, RFCs and guidelines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{General and reference~Computing standards, RFCs and guidelines}`\label{l:ccs:end}`

\maketitle

\begin{abstract}
  This paper shows...
\end{abstract}

\section{Introduction}
The art of computer programming~\cite{DBLP:journals/cacm/Knuth74}...
\section{...}
...
\acks`\label{l:acks}`
I want to thank ....

\printbibliography
\end{document}
\end{lstlisting}

{\lstset{language=}%
  We have included a most minimal article in \autoref{lst:tour} that you can
  adapt to the concrete work to be submitted. First, you
  have to select the \lstinline|programming| class as in \autoref{l:doc}. The
  parameter \lstinline|english| is for language selection (optional, but
  recommended). The other parameter, \lstinline|submission|, is crucial for the
  reviewing process and must be included for submission. More information on
  document parameters can be found in \autoref{sec:class-options}. After that,
  we recommend that you load the \lstinline|biblatex| package. While it is %
  perfectly fine to use plain {BibTeX}, we recommend
  \lstinline|biblatex|, as it has native Unicode support and can handle
  \textsc{url}s and \textsc{doi}s better. In both cases, we have preloaded a
  bibliography style.

  At that point, you can load necessary {LaTeX} packages. We already load some
  important packages with the \lstinline|programming| class and that there are
  certain packages that are not recommended or incompatible with this class.
  Refer to \autoref{sec:pack-cons} for which packages are recommended. The you
  start the document with \lstinline|\begin{document}|.

  You have to provide details to your submission that will be used during the
  review process. For that, use the \lstinline|paperdetails| command and
  specify \emph{perspective} and \emph{area} of your submission. For
  perspective, choose form one of the \emph{Art}, \emph{theoretical} or
  \emph{empirical} \emph{Science}, or \emph{Engineering} and provide it as
  argument to the \lstinline|perspective| keyword; they can be found in
  \autoref{sec:perspective}. For area, specify an argument to the
  \lstinline|area| keyword (in braces). Find a list of suggested areas in
  \autoref{sec:area-submission}.

We need you to provide certain metadata which you can do with the following
commands, as form \autoref{l:meta}. You can specify the title and maybe the subtitle with
\lstinline|\title| (and \lstinline|\subtitle|, respectively). Then please
list all authors. For that, use one \lstinline|\author| command per author
and give an affiliation for each with \lstinline|\affiliation|. When several
consecutive authors share the same affiliation, you should only use one
\lstinline|\affiliation| command after the last of them. More information can
be found in \autoref{sec:document-metadata}.

Please include one to five keywords, separated by commas, that are important to
your work with the \lstinline|\keywords| command as in \autoref{l:keywords}. We
kindly ask you to classify your work using the \emph{ACM Computing
  Classification System}\footnote{\url{https://dl.acm.org/ccs/ccs.cfm}.}.
Please visit the ACM's website and generate the {TeX} code that matches
your classification. The code should consist of a \lstinline|CCSXML|
environment and several \lstinline|\ccsdesc| commands, as in lines
\ref{l:ccs:start} to \ref{l:ccs:end}.

With \lstinline|\maketitle| and the \lstinline|abstract| environment, you can
produce the article's title page. Then you can start with your content. If
applicable, you can put acknowledgements at the end after an \lstinline|\acks|
command, as in \autoref{l:acks}.}

\subsection{Running {LaTeX}}
\label{sec:running}

This class has been tested with the popular {LaTeX} programs available.
It should work with {pdfLaTeX}, {LuaLaTeX}, and {XeLaTeX}.
We suggest that you use {LuaLaTeX}, which is included in all major
{TeX} system installations, has a good Unicode support, and is well portable.
Please do not use the LaTeX/dvips combination to produce output files.
To get all metadata right, several LaTeX runs will be necessary. Hence, a
typical run looks like this:
\begin{lstlisting}[language=]
lualatex myarticle
biber myarticle
lualatex myarticle
lualatex myarticle
\end{lstlisting}

You should replace \lstinline|lualatex| with the LaTeX program of your choice,
and \lstinline|biber| with \lstinline|bibtex| if you do not want to use
Biblatex (or use Biblatex's BibTeX backend).

Your \textsc{pdf} file for your article should then be ready for submission.

\section{Submission Classification}

Almost anything about programming is in scope for The Art, Science, and
Engineering of Programming. However, you should classify your article according
to the following aspects.

\subsection{Perspective}
\label{sec:perspective}

We accept descriptions of work under different perspectives:

\emph{The Art.} This perspective is about knowledge and technical skills acquired through
practice and personal experiences. Examples include libraries, frameworks,
languages, APIs, programming models and styles, programming pearls, and essays
about programming.

\emph{Science (theoretical).} This perspective is about knowledge and technical skills acquired
through mathematical formalisms. Examples include formal programming models and
proofs.

\emph{Science (empirical).} This perspective is about knowledge and technical skills acquired
through experiments and systematic observations. Examples include user studies
and programming-related data mining.

\emph{Engineering.} This perspective is about knowledge and technical skills acquired through
designing and building large systems and through calculated application of
principles in building those systems. Examples include measurements of
artifacts’ properties, development processes and tools, and quality assurance
methods.

\bigskip
To classify your work as any of the above perspectives, please set the
\lstinline|perspective| keyword of  the \lstinline|\paperdetails| command to
one of the following values:

\begin{description}
\item[art] for submissions concerning \emph{The Art } (\textsf{theart} is a
  proper alias);
\item[sciencetheoretical] For submissions concerning \emph{Science
    (theoretical)}, with the aliases \textsf{sciencetheoretical},
  \textsf{theoreticalscience}, \textsf{theoretical},
  \textsf{science-theoretical}, and finally \textsf{theoretical-science};
\item[scienceempirical] for submissions concerning \emph{Science (empirical)},
  the valid aliases are \textsf{scienceempirical}, \textsf{empiricalscience},
  \textsf{empirical}, \textsf{science-empirical}, and
  \textsf{empirical-science}; and
\item[engineering] for submissions concerning \emph{Engineering}.
\end{description}

\subsection{Area of Submission}
\label{sec:area-submission}

Independent of the type of work, the journal accepts submissions covering
several expertise areas. Expertise areas include, but are not limited to:

\begin{itemize}
\item General-purpose programming
\item Distributed systems programming
\item Parallel and multi-core programming
\item Graphics and GPU programming
\item Security programming
\item User interface programming
\item Database programming
\item Visual and live programming
\item Data mining and machine learning programming, and for programming
\item Interpreters, virtual machines and compilers
\item Modeling and modularity
\item Testing and debugging
\item Program verification
\item Programming education
\item Programming environments
\item Social coding
\end{itemize}

To specify the area of expertise for your work, please set the
\lstinline|area| keyword of  the \lstinline|\paperdetails| command to
one of the preceding suggested areas, or provide your own. Please use curly
braces \lstinline|{}| around the value.

\section{Choice of License (optional)}

All work published by The Art, Science, and Engineering of Programming will be
available as open-access. Therefore, authors submitting a paper to The Art,
Science, and Engineering of Programming should grant a Creative Commons
license. We support two licenses (description adapted from
Wikipedia\footnote{\url{https://en.wikipedia.org/w/index.php?title=Creative_Commons_license&oldid=754498632}}):
\begin{description}
\item[\ccby] \href{https://creativecommons.org/licenses/by/4.0}{Attribution 4.0
    \textsmaller{\textsc{cc by 4.0}}}\\
  {\small
    Licensees may copy, distribute, display and perform the work and make
    derivative works and remixes based on it only if they give the author or
    licensor the credits (attribution) in the manner specified by these.}
  \item[\ccbync]
  \href{https://creativecommons.org/licenses/by-nc-sa/4.0}{Attribution-NonCommercial
    4.0 \textsmaller{\textsc{cc by-nc 4.0}}}\\
  {\small
  Licensees may copy, distribute, display and perform the work and make
  derivative works and remixes based on it only if they give the author or
  licensor the credits (attribution) in the manner specified by these and only
  for non-commercial purposes.}
\end{description}
%
To choose a license for your work, set the
\lstinline|license| keyword of  the \lstinline|\paperdetails| command to
either \lstinline|cc-by| or \lstinline|cc-by-sa|. Please be aware that, in absence of a choice, we assume \textsc{cc by}.

\section{Typographical and Technical Aspects}

We have carefully chosen the presentation for articles published in The Art, Science, and
Engineering of Programming to fit on-screen reading and occasional printouts.
It is important to maintain a uniform look of all articles appearing in the
journal. We kindly ask you therefore to \emph{not} change the presentation. Most
importantly,
%
\begin{itemize}
\item please do not change the font or the font size for that matter. The text
  font remains fixed as \emph{Charter} (in the XCharter variant) and emphasis
  font is \emph{Fira Sans}. The only exception is the typewriter font, where
  you can choose from two variants (please refer to
  \autoref{sec:typewriter-fonts}). Moreover;
\item please do not change the margins or the line spacing;
\item please refrain from using the \lstinline|\sloppy| command, especially for
  the whole document;
\item please avoid the use of the \lstinline|[H]| or \lstinline|[h!]| modifiers
  for figures, tables, and similar elements;
\item please use a consistent formatting  (for example, use the
  \lstinline|siunitx| package~\cite{siunitx}).
\end{itemize}
%
This class has been tested on several LaTeX systems. We suggest that you use an
up-to-date system, for example
TeX\,Live\footnote{\url{https://www.tug.org/texlive/}.}, which is available for
Linux, Windows, and Apple systems, among others. We tested with the 2015 and
2016 systems and will make sure that it will work with upcoming systems, too.
Please first upgrade your system if problems with this class should occur.
Regarding the LaTeX system, please keep in mind to
%
\begin{itemize}
\item use LaTeX packages only if required, as fewer packages lower the
  chance of conflicts (refer to \autoref{sec:pack-cons} for details);
\item keep the use of custom macros low to not interfere with provided
  packages and use LaTeX commands to do so (for example, \lstinline|\newcommand| and
  similar instead of TeX's \lstinline|\def|);
\item watch out for unsuitable line- and pagebreaks;
\item when using pixel graphics, provide at least 300\,dpi imagery,
  \textsc{pdf} files preferred;
\item minimize the use of LaTeX comments, especially via block constructs;
\item consult the \emph{l2tabu} documentation~\cite{l2tabu} about outdated packages;
\item provide \textsc{doi}s for all your references, unless inaccessible.
\end{itemize}
%
We suggest the use of a spellchecker to avoid typos.

Please note that all article source must be \textsc{utf-8} encoded, no
exceptions.

\section{Detailed Reference}

Several aspects of this class as outlined above provide for some fine tuning.

\subsection{Class Options}
\label{sec:class-options}

As explained in~\autoref{sec:guided-tour}, submissions to the journal must use
the \lstinline|submission| package option. For the accepted final, to-be-published
version, this option should be omitted or replaced by  \lstinline|crc| for
“Camera-ready Copy”. Actually, both are shortcuts for the
\lstinline|phase| keyword, which could be used, instead.
Hence, the following statements in either column are equivalent:\par\noindent
{\lstset{texcsstyle=*{\color{Purple}\mdseries\smaller}}
\begin{minipage}[t]{.45\linewidth}
\emph{Final phase}
\begin{lstlisting}
\documentclass[phase=final]{programming}
\documentclass[crc]{programming}
\documentclass{programming}
\end{lstlisting}
\end{minipage}%
\hfill%
\begin{minipage}[t]{.5\linewidth}
\emph{Submission phase}
\begin{lstlisting}[numbers= none]
\documentclass[phase=submission]{programming}
\documentclass[submission]{programming}
``
\end{lstlisting}
\end{minipage}}

\paragraph{Code Fonts}
\label{sec:typewriter-fonts}

The standard font for code, as selected with \lstinline|\texttt|,
\lstinline|\ttfamily|, or a listing, is set to be the same as the sans serif
font, \emph{Fira Sans}. This matches the rest of the document style very well.
However, it may be strictly necessary to have a non-proportional (or
monospaced) font for the typewriter style. We therefore provide a class option \lstinline|code|
to change the typewriter font.
It takes one the following values:
\begin{description}
\item[code=sf] Sets the code font to the sans serif font (Fira Sans). This is the
  default. Aliases for this option are \lstinline|code=sans| and
  \lstinline|code=sansserif|.
\item[code=tt] Sets the code font to Fira Sans' monospaced equivalent, Fira Mono. Aliases for this option are \lstinline|code=mono| and
  \lstinline|code=monospace|. This is the preferred choice if monospaced
  typewriter font is necessary. Note that this font does not have italics.
\end{description}

\paragraph{Other Options}

All other options give in the \lstinline|\documentclass| command are not
processed directly by the class but rather passed on to other packages as
``global options''. For example, the \lstinline|english| option from the
example above does not influence the \lstinline|programming| class directly,
but rather will be picked up by Babel~\cite{babel} to set up language options.

\subsection{Document Metadata}
\label{sec:document-metadata}

The presentation of the document metadata can be fine tuned, as well.
Besides the \lstinline|\title| and \lstinline|\subtitle| commands, there is the
\lstinline|\titlerunning| command to specify a shorter title when the normal
title does not fit into the page header. Similarly, the
\lstinline|\authorrunning| command can be used to specify the presentation of
the authors in the header.

Sometime listing the affiliations of the authors can be tricky when they are
shared. An optional argument to the \lstinline|\author| and
\lstinline|\affiliation| command can be used to associate authors and
affiliations explicitly. Four variants for affiliations are outlined in the
beginning of \autoref{lst:affiliation}.

For the final publication, we ask you to provide a short information of each
author, typically a very short biography, and a photo. You can use the
\lstinline|\authorinfo| command right after an \lstinline|\author| command to
associate that author information with an author. See \autoref{l:authorinfo} in
\autoref{lst:affiliation} for example. The photo is given as optional argument
as file name in brackets (without file extension). Omitting the photo will
produce a blank space next to the author information. The actual information
follows as an argument. Note that the author's \emph{name} is prepended to the
information automatically and is not to be repeated.

An author's email address can be given in either the affiliation or author
information block. Please use the \lstinline|\email| command for that purpose.

\begin{lstlisting}[float,label=lst:affiliation,caption={Four
ways to specify affiliations\,/\,Author information example\,/\,Sample publication paper details}]
% Independent affiliations
\author{Anna Author}
\affiliation{The Unseen University, Ankh-Morpork}
\author{Bert Betatester}
\affiliation{Carolingian Minuschool Academy, Bodoni, San Serriffe}

% Shared affiliations
\author{Anna Author}
\author{Bert Betatester}
\affiliation{Carolingian Minuschool Academy, Bodoni, San Serriffe}

% Explicit affiliations
\author[a]{Anna Author}
\author[b]{Bert Betatester}
\author[a]{Claire Cadence}
\affiliation[a]{The Unseen University, Ankh-Morpork}
\affiliation[b]{Carolingian Minuschool Academy, Bodoni, San Serriffe}

% Mixed affiliations
\author[a]{Anna Author}
\author[a,b]{Bert Betatester}
\affiliation[a]{The Unseen University, Ankh-Morpork}
\affiliation[b]{Carolingian Minuschool Academy, Bodoni, San Serriffe}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Author information`\label{l:authorinfo}`
\author{Anna Author}
\authorinfo[anna]{is a researcher at the Unseen University in Ankh-Morpork and
a Ph\,D student to Rincewind. Contact her at
\email{anna.the.author@univ-unseen.edu.pratchett}}
\affiliation[a]{The Unseen University, Ankh-Morpork}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Sample publication paper details
\paperdetails{
  submitted=2017-02-18,
  published=2017-08-01,
  year=2017,
  volume=2,
  issue=1,
  articlenumber=4,
}
\end{lstlisting}

\subsection{Paper Details}

Besides specifying the perspective and area of the submission, the
\lstinline|\paperdetails| command is also used to provide publication
information for the final, camera-ready-copy phase (class option
\lstinline|phase=final|). In this case, perspective and area are removed from
the title page and the Digital Object Identifier (\textsc{doi}), as well as the
dates of submission and publications are presented instead. The information
necessary for this is provided \emph{by the publisher} after acceptance. It
includes the following information:
%
\begin{description}
\item[year] The year of the articles publication.
\item[volume] The volume the article appears in.
\item[issue] The issue the article appears in.
\item[articlenumber] The number of the article within the volume.
\item[submitted] The date the article was submitted to (and received by) the
  publisher. Please use an \textsc{iso} date (\textsc{yyyy-mm-dd}).
\item[published] The date the article was published and made public by the
  publisher. Please use an \textsc{iso} date (\textsc{yyyy-mm-dd}).
\end{description}
%
See the end of \autoref{lst:affiliation} for an example.

\subsection{Figures, Tables, Listings}

Sometimes it is necessary to pay special attention to the \emph{floating
  elements} of your document, that is figures, tables, listings, and similar.
While it is tempting to force those elements to the specific position where
they are written down, this is not always the best choice, especially since it
can interrupt the reading flow. Therefore please refrain form using the
\lstinline|[h!]| and  \lstinline|[H]| specifiers for such elements. If you
\emph{must} have the element at the current position, it maybe is not a
\emph{floating element}, in the first place. It is perfectly fine to use
graphics \emph{without} a \lstinline|\begin{figrue}...\end{figure}| environment
or use a \lstinline|\begin{tabular}...\end{tabular}| \emph{without} an
enclosing \lstinline|\begin{table}...\end{table}|.

\begin{table}
  \centering
  \caption{Differences between things projected and things achieved}
  \label{tbl:things}
  \begin{threeparttable}
    \footnotesize
    \begin{tabular}{>{}p{.33\linewidth}@{}cSs}
      \toprule
      Part           & done & {Value}   & Unit                      \\
      \midrule
      Title          & yes  &    2.3456 & \dB                       \\
      Abstract   &  yes  &       e3  & \kilo\hertz               \\
      \midrule
      \multicolumn{4}{c}{Rest is not entirely true}                 \\
      \midrule
      Context        & yes  &   90.473  & \percent                  \\
      Problem        & no\tnote{a} &    &                           \\
      Solution       & yes  & 5642.5    & \mega\byte                \\
      Implementation & yes  &    1.2e-3 & \metre\squared\per\second \\
      Evaluation     & no   &           &                           \\
      Related Work   & no   &           &                           \\
      Conclusion     & yes  &    4955.3 & \per\kilogram             \\
      \bottomrule
    \end{tabular}
    \begin{tablenotes}
    \item [a] Just a few things missing
    \end{tablenotes}
  \end{threeparttable}
\end{table}

The caption position of a floating element should match its content. For
tables, listings, algorithms, or similar list-like content, please use captions
\emph{above} its contents, as those elements are typically read from top to
bottom. Find examples in the listings already presented and
\autoref{tbl:things}. For figures, graphs, graphics, or similar, please us
captions \emph{below} the imagery, as in \autoref{fig:test}.

For tabular content, we suggest to avoid vertical lines altogether and keep
horizontal lines to a minimum. Refer to the \lstinline|booktabs| package
documentation for more information~\cite{booktabs}. Also, the
\lstinline|threeparttable| package is valuable if you need footnotes in your
table~\cite{threeparttable}.

\subsection{Bibliography}

As outlined, the \lstinline|programming| class supports both plain BibTeX as
well as the newer Biblatex bibliography package to present your references.
Please note that you may not change the bibliography style, it is pre-selected
by the class. It is a simple, numbered style with all references sorted
alphabetically. In text, it should look like
this:~\cite{DBLP:journals/cacm/Knuth74}. Note that the reference has the
\textsc{doi} included. We would like to encourage you to always provide the
\textsc{doi}s of the works you cite, if possible. However, please make sure in
your bibliography file, that the \lstinline|doi| entry is a plain entry without
a ``resolver'' (for example, \textsf{http://dx.doi.org/}) prepended. A typical
example for an entry format should look like in \autoref{lst:bib}. Please
shorten neither names nor journal articles, if possible.

The bibliography commands for your article should look like this (for Biblatex
and plain BibTeX, respectively):\\*
\begin{minipage}[t]{.45\linewidth}
\emph{Biblatex}
\begin{lstlisting}
\documentclass{programming}
\usepackage[backend=biber]{biblatex}
\addbibresource{example.bib}
\begin{document}
...
\printbibliography
\end{document}
\end{lstlisting}
\end{minipage}%
\hfill%
\begin{minipage}[t]{.45\linewidth}
\emph{Plain  BibTeX}
\begin{lstlisting}[numbers= none]
\documentclass{programming}

\begin{document}
...
\bibliography{example}
\end{document}
\end{lstlisting}
\end{minipage}

\begin{lstlisting}[float,label=lst:bib,language=,caption={A typical BibTeX entry for \cite{DBLP:journals/cacm/Knuth74}}]
@article{DBLP:journals/cacm/Knuth74,
  Author = {Donald E. Knuth},
  Doi = {10.1145/361604.361612},
  Journal = {Communications of the {ACM}},
  Number = {12},
  Pages = {667--673},
  Title = {{Computer Programming as an Art}},
  Volume = {17},
  Year = {1974}}
\end{lstlisting}

\subsection{{LaTeX} Packages Considerations }
\label{sec:pack-cons}

The following packages are automatically loaded by the \lstinline|programming|
class and need not to be loaded manually.

\begin{multicols}{4}
{\color{DarkGreen}
\begin{itemize}
\item \path{accsupp}
\item \path{amsmath}
\item \path{amstext}
\item \path{array}
\item \path{atbegshi}
\item \path{babel}
\item \path{booktabs}
\item \path{calc}
\item \path{caption}
\item \path{colortbl}
\item \path{comment}
\item \path{csquotes}
\item \path{doclicense}
\item \path{expl3}
\item \path{FiraSans}
\item \path{fnpct}
\item \path{fontspec}
\item \path{fontenc}
\item \path{gettitlestring}
\item \path{graphics}
\item \path{graphicx}
\item \path{grfext}
\item \path{hypcap}
\item \path{hyperref}
\item \path{hyperxmp}
\item \path{listings}
\item \path{mathdesign}
\item \path{microtype}
\item \path{morewrites}
\item \path{multirow}
\item \path{relsize}
\item \path{rotating}
\item \path{siunitx}
\item \path{subcaption}
\item \path{tabularx}
\item \path{textcase}
\item \path{textcomp}
\item \path{threeparttable}
\item \path{typearea}
\item \path{url}
\item \path{verbatim}
\item \path{xcolor}
\item \path{xparse}
\item \path{xspace}
\item \path{xunicode}
\end{itemize}}
\end{multicols}

\par\noindent The following packages \emph{must not} be loaded.

\begin{multicols}{4}
{\color{DarkRed}
\begin{itemize}
\item \path{SIstyle}
\item \path{SIunits}
\item \path{a4wide}
\item \path{a4}
\item \path{aecompl}
\item \path{ae}
\item \path{caption2}
\item \path{courier}
\item \path{doublespace}
\item \path{epsfig}
\item \path{epsf}
\item \path{euler}
\item \path{fancyhdr}
\item \path{fancyheadings}
\item \path{fourier}
\item \path{geometry}
\item \path{glossary}
\item \path{helvet}
\item \path{isolatin}
\item \path{mathpple}
\item \path{mathptmx}
\item \path{mathptm}
\item \path{newtxmath}
\item \path{newtxtext}
\item \path{palatino}
\item \path{psfig}
\item \path{pslatex}
\item \path{scrpage}
\item \path{subfigure}
\item \path{subfig}
\item \path{t1enc}
\item \path{times}
\item \path{umlaut}
\item \path{utopia}
\item \path{zefonts}
\end{itemize}}
\end{multicols}
%
\noindent
Additionally, any package that changes the font must not be loaded.

\acks
We want to thank you for using this class to prepare articles for The Art, Science, and Engineering of Programming.
\printbibliography

\appendix
\section{A Famous Filler Text}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis
nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu
fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum.

\section{Submission Checklist}
\begingroup
\smaller
\begin{itemize}
\renewcommand*\labelitemi{\ensuremath{\square}}
\item All authors are listed, with affiliation
\item The abstract is not longer than 500 words.
\item The abstract states, in this order, \emph{Context},
  \emph{Inquiry}, \emph{Approach}, \emph{Knowledge}, \emph{Grounding}, and
  \emph{Importance} of the submission.
\item The ACM CCS 2012 classification is included.
\item A list of relevant keywords is provided.
\item One \emph{perspective} has been chosen.
\item One or more \emph{area(s) of submission} have been chosen.
\item The license has been acknowledged or changed to fit.
\item The title page does not spill onto the second page.
\item The running title on even pages' heads is not wider than the text block.
\item The running list of author on odd pages' heads is not wider than the text
  block.
\item The only text encoding used is \textsc{utf-8}.
\item The fonts, margins, and spacings are unchanged.
\item All \textsc{url}s are marked using the \lstinline|\url| command.
\item All units are separated from their values with a half space, consistently
  (see ~\cite{siunitx}).
\item Bold font is not used (or only in exceptional circumstances).
\item Underlining is not used (no exceptions).
\item Bold or bright colors are only ever used sparingly.
\item The captions of (a) tables, (b) listings, and (c) algorithms are
  \emph{above} the content, flush left.
\item The captions of (a) figures, (b) charts, (c) combined content, and
  similar are \emph{below} the content, flush left.
\item %
  \begin{minipage}[t]{.4\linewidth}
    Tables adhere to best practice layout~\cite{booktabs}. The do not contain
  vertical lines and only few horizontal lines.
  \end{minipage}
  {\renewcommand{\arraystretch}{.6}
    \hspace{2em} \textcolor{DarkGreen}{Yes} \hspace{1em}
      \begin{tabular}[t]{ll}\noalign{\vspace*{-2.2ex}}
        \toprule
        \emph{a} & \emph{b}\\
        \midrule
        x & abc \\
        y & def \\
        \bottomrule
      \end{tabular}
      \hspace{2em} \textcolor{DarkRed}{No} \hspace{1em}
      \begin{tabular}[t]{|l|l|}\noalign{\vspace*{-1.6ex}}
        \hline
        \emph{a} & \emph{b}\\
        \hline\hline
        x & abc \\\hline
        y & def \\\hline
      \end{tabular}}
\item All fonts are embedded. This includes the fonts for any included
  (\textsc{pdf}-)graphics.
\item All graphics are either vector graphics or have at least 300\,dpi.
  \item Acknowledgements, including statement of funding bodies or projects, is
  placed before the references, using the \lstinline|\acks| command.
\item Citations in the text are preceded by a non-breaking space.
  (\(\rightarrow\) Citations do not appear at the beginning of a line)
\item The bibliography lists all cited works, all authors are given (no
  \emph{et. al.}), the full names of the authors are used.
\item All bibliography entries have a \textsc{doi} (unless not applicable, such as for
  slides or unpublished work).
\item All bibliography entires show an \textsc{isbn}, if they have one assigned.
\item All bibliography entires that represent web sites have a \textsc{url} and
  an \emph{access date}.
\item No bibliography entry have duplicate information in \textsc{url} and
  \textsc{doi}.
\end{itemize}
%
For the final phase (or camera-ready copy), additionally:
\begin{itemize}
\renewcommand*\labelitemi{\ensuremath{\square}}
\renewcommand*\labelitemii{\ensuremath{\square}}
\item The \lstinline|\paperdetails| are included as provided by the journal.
\item The \textsc{doi}, and submission and publication date appear on the title
  page.
\item Neither the \emph{perspective} nor the \emph{area of submission} appear
  on the title.
\end{itemize}

\endgroup

\end{document}

% Local Variables:
% TeX-engine: luatex
% End:

### 2021-08-02 compile-latex.sh

@@ -1,0 +1,18 @@
+set -e
+
+pandoc \
+  --filter conditional-render \
+  --filter pandoc-crossref \
+  -s \
+  -o \
+  paper.tex \
+  --natbib \
+  --template=ieee.pandoc \
+  --metadata=format:pdf \
+  paper.md
+
+pdflatex paper.tex
+bibtex paper
+pdflatex -interaction=batchmode paper.tex
+pdflatex -interaction=batchmode paper.tex
+cp paper.pdf index.pdf

### 2021-08-02 paper.tex
First pass to get paper under 6 pages

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage[sort, numbers]{natbib}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%%
+%% IMPORTANT NOTICE:
+%%
+%% For the copyright see the source file.
+%%
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%%
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%%
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf,10pt]{acmart}
 
-% Make font size smaller in bibliography, as per:
-% https://tex.stackexchange.com/questions/386709/proper-usage-of-biblatex-ieee-biblatex-style-in-an-ieeetran-document
-\renewcommand*{\bibfont}{\footnotesize}
-
-% begin pandoc tex stuff
+\settopmatter{printfolios=true}
 
@@
 
-% end pandoc tex stuff
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
 
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+\pagenumbering{gobble}
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
 
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
 \title{Joker: A Unified Interaction Model For Web Customization}
 
-% removing authors for anonymous submission
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
 
-% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-% \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
-% \and
-% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-% \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
-% \and
-% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-% \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
-% \and
-% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-% \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}}
+%\author{Kapaya Katongo}
+%\affiliation{%
+%  \institution{MIT CSAIL}
+%  \city{Cambridge, MA}
+%  \country{USA}
+%}
+%\email{kkatongo@mit.edu}
 
+%\author{Geoffrey Litt}
+%\affiliation{%
+%  \institution{MIT CSAIL}
+%  \city{Cambridge, MA}
+%  \country{USA}
+%}
+%\email{glitt@mit.edu}
+
+%\author{Kathryn Jin}
+%\affiliation{%
+%  \institution{MIT CSAIL}
+%  \city{Cambridge, MA}
+%  \country{USA}
+%}
+%\email{kjin@mit.edu}
+
+%\author{Daniel Jackson}
+%\affiliation{%
+% \institution{MIT CSAIL}
+%  \city{Cambridge, MA}
+%  \country{USA}
+%}
+%\email{dnj@csail.mit.edu}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
+%% \begin{abstract}
+%%  
+%% \end{abstract}
+
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+%% From HERE
+%%\begin{CCSXML}
+%%<ccs2012>
+%%<concept>
+%%<concept_id>10011007.10011006.10011066.10011069</concept_id>
+%%<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
+%%<concept_significance>500</concept_significance>
+%%</concept>
+%%</ccs2012>
+%%\end{CCSXML}
+
+%% \ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
+% To HERE
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+%% \keywords{end-user programming, software customization, web scraping, programming-by-example, program synthesis}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+% \begin{teaserfigure}
+%  \includegraphics[width=\textwidth]{sampleteaser}
+%  \caption{Seattle Mariners at Spring Training, 2010.}
+%  \Description{Enjoying the baseball game from the third-base
+%  seats. Ichiro Suzuki preparing to bat.}
+%  \label{fig:teaser}
+%\end{teaserfigure}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
 \maketitle
-
-\begin{abstract}
-Tools that enable end-users to customize websites typically use a
-two-stage workflow: first, users extract data into a structured form;
-second, they use that extracted data to augment the original website in
-some way. This two-stage workflow poses a usability barrier because it
-requires users to make upfront decisions about what data to extract,
-rather than allowing them to incrementally extract data as they augment
-it.
-
-In this paper, we present a new, unified interaction model for web
-customization that encompasses both extraction and augmentation. The key
-idea is to provide users with a spreadsheet-like formula language that
-can be used for both data extraction and augmentation. We also provide a
-programming-by-demonstration (PBD) interface that allows users to create
-data extraction formulas by clicking on elements in the website. This
-model allows users to naturally and iteratively move between extraction
-and augmentation.
-
-To illustrate our unified interaction model, we have implemented a tool
-called Joker which is an extension of Wildcard, a prior web
-customization system. Through case studies, we show that Joker can be
-used to customize many real-world websites. We also present a formative
-user study with five participants, which showed that people with a wide
-range of technical backgrounds can use Joker to customize websites, and
-also revealed some interesting limitations of our approach. Finally, we
-present a heuristic evaluation of our design using the Cognitive
-Dimensions framework.
-\end{abstract}
-
-\begin{IEEEkeywords}
-end-user web customization, programming-by-demonstration, spreadsheets, end-user web scraping, program synthesis
-\end{IEEEkeywords}
 
@@
 formula language and user interface, as well as the algorithms used by
-our PBD interface.
-
-We have performed three evaluations of our approach, presented in
-Section~\ref{sec:evaluation}. First, we describe a suite of case studies
-in which we used Joker to extract and augment a variety of websites in
-order to characterize its capabilities and limitations. Second, we
-describe a formative user study with five participants, which showed
-that users were generally able to use Joker to perform useful extraction
-and augmentation tasks, but which also uncovered limitations,
-particularly for less experienced users trying to extract data from more
-complex websites. Finally, we perform a heuristic evaluation of our
-design, using the Cognitive Dimensions \citep{blackwell2001} framework.
-
-Joker relates to existing work not only in end-user web customization,
-but also in end-user web scraping and program synthesis, which we
-discuss in Section~\ref{sec:related-work}. Finally, we discuss
-opportunities for future work in Section~\ref{sec:conclusion}.
+our PBD interface. We evaluate our approach in
+Section~\ref{sec:evaluation} by describing a suite of case studies in
+which we used Joker to extract and augment a variety of websites in
+order to characterize its capabilities and limitations. Joker relates to
+existing work not only in end-user web customization, but also in
+end-user web scraping and program synthesis, which we discuss in
+Section~\ref{sec:related-work}. Finally, we discuss opportunities for
+future work in Section~\ref{sec:conclusion}.
 
@@
 In this section, we describe Joker's formula language in more detail.
-Then, we outline the \emph{wrapper induction} \citep{kushmerick2000}
-algorithm that Joker's PBD interface uses to synthesize the row element
-and column selectors presented in formulas. Figure~\ref{fig:overview}
-illustrates the entire process.
+Then, we briefly outline the \emph{wrapper induction}
+\citep{kushmerick2000} algorithm that Joker's PBD interface uses to
+synthesize the row element and column selectors presented in formulas.
 
@@
 implemented a set of heuristics inspired by Vegemite \citep{lin2009} for
-wrapper induction, described below.
-
-\hypertarget{determining-row-elements}{%
-\subsubsection{Determining Row
-Elements}\label{determining-row-elements}}
-
-The user starts by demonstrating an element \(v\), representing a value
-that should be in the table. From that demonstration, we must find a set
-of \emph{row elements} that represent the rows of the table. We could
-naively assume that \(parent(v)\) is the row containing \(v\), but often
-\(v\) is deeply nested inside its containing row; we must determine
-which ancestor of \(v\) is likely to be the row.
-
-Intuitively, we solve this problem by assuming that all rows share some
-similar internal structure. In particular, we expect most rows to
-contain a value for the demonstrated column. (If there were no missing
-data, we'd expect \emph{all} rows to contain data for this column.)
-
-Formally: assume a function \(select(el, s)\) which runs a CSS selector
-that returns the set of elements matching \(s\) within \(el\). We
-generate a set of plausible candidates \(P\), consisting of pairs of a
-row element and a CSS selector:
-
-\(P = \{ (r, s) \mid r \in ancestors(v) \land select(r, s) = \{v\} \}\)
-
-For each candidate \((r, s) \in P\), we compute a weight function \(w\),
-which is based on the number of siblings of \(r\) that have ``similar
-structure'', defined by checking whether running \(s\) within the
-sibling also returns a unique element.
-
-\(w(r, s) = |\{ r' \mid r' \in siblings(r) \land |select(r', s) | = 1 \}|\)
-
-We then choose the candidate with the highest weight. In case of ties,
-the candidate closer to \(v\) in the tree (i.e., lower in the tree)
-wins. Given a winning candidate \((r, s)\), the full set of row elements
-is \(\{r\} \cup siblings(r)\).
-
-\hypertarget{synthesizing-css-selectors-for-column-values}{%
-\subsubsection{Synthesizing CSS Selectors For Column
-Values}\label{synthesizing-css-selectors-for-column-values}}
-
-Once we have determined the row elements, next we must choose a CSS
-selector that will be used to identify the demonstrated value within its
-row.
-
-Given a demonstrated value \(v\) within a row element \(r\), we generate
-two kinds of plausible selectors:
-
-\begin{itemize}
-\tightlist
-\item
-  selectors using CSS classes, which are manual annotations on DOM
-  elements added by the website's programmers, typically for styling
-  purposes (e.g.~"item\_\_price")
-\item
-  selectors using positional indexes within the tree, using the
-  \texttt{nth-child} CSS selector (e.g.~\texttt{nth-child(2)},
-  representing the second child of an element)
-\end{itemize}
-
-The minimum criteria for a plausible selector \(s\) is that it uniquely
-identifies the value within the row: \(select(r, s) = \{v\}\). But there
-may be many plausible selectors, so we must pick a best one.
-
-We first prioritize selectors using classes, because they tend to be
-more robust to changes on the website. A single selector can combine
-multiple classes, but we prefer using fewer classes when possible. If no
-plausible class-based selector can be generated (for example, if the
-relevant elements don't have any classes to query), we fall back to
-using a positional index selector. This kind of selector can always be
-generated regardless of the contents of the page, but tends to be less
-accurate and robust.
+wrapper induction, illustrated in Figure~\ref{fig:overview}.
 
@@
 
-We evaluate our interaction model and tool in terms of three research
-questions:
-
-\emph{RQ1: What kinds of websites can this model operate effectively
-on?} We evaluate this with a suite of case studies that demonstrate its
-capabilities and limitations.
-
-\emph{RQ2: How are users of different backgrounds able to use the
-system?} We evaluate this with a small formative user study.
-
-\emph{RQ3: What are the essential design dimensions that distinguish
-this model from other approaches?} We evaluate this with a heuristic
-analysis using the Cognitive Dimensions of Notation framework
-\citep{blackwell2001}.
-
-\hypertarget{case-studies}{%
-\subsection{Case Studies}\label{case-studies}}
-
-Our first evaluation describes the results of the authors using Joker to
-extract data and perform customizations on popular websites. For the
-websites on which Joker can be used, we provide the sequence of
-interactions needed to achieve the customizations; for the websites on
-which Joker fails, we explain the relevant limitations.
+We evaluate our interaction model and tool by describing the results of
+our use of Joker to extract data and perform customizations on popular
+websites. For the websites on which Joker can be used, we provide the
+sequence of interactions needed to achieve the customizations; for the
+websites on which Joker fails, we explain the relevant limitations.
 
 \hypertarget{successful-applications}{%
-\subsubsection{Successful Applications}\label{successful-applications}}
-
-\begin{table*}[]
-\centering
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Website}              & \textbf{Example Customization Achieved by Joker}                                        \\ \hline
-eBay, Amazon            & Filter listings by whether they have a "Sponsored" label.                        \\
-Amazon, Target & Sort search results by price and rating.                                                \\
-Google Scholar                & Filter publications for those whose title contains a user-provided keyword. \\
-Reddit, CNN, ABC  & Sort by the read times of articles. Filter already-visited articles.         \\
-Weather.com                   & Filter hourly weather to find sunny times of day.                                        \\
-Github                        & Sort a user's code repositories by stars to find popular work.                          \\
-Postmates, Uber Eats    & Sort restaurants by delivery time and delivery fee.                                     \\ \hline
-\end{tabular}
-\vspace{8pt}
-\caption{Examples of websites that Joker can be used to customize, including extraction and augmentation}
-\end{table*}
+\subsection{Successful Applications}\label{successful-applications}}
 
@@
 Then, the user can write the formula \texttt{Includes(A,\ "compiler")}
-that returns whether or not the title contains the keyword ``compiler''.
+that returns whether or not the title contains the keyword ``compiler.''
 Finally, the user can sort by this column to get all of the publications
@@
 \hypertarget{limitations}{%
-\subsubsection{Limitations}\label{limitations}}
+\subsection{Limitations}\label{limitations}}
 
@@
 
-\hypertarget{user-study}{%
-\subsection{User Study}\label{user-study}}
-
-We conducted a small formative user study to understand how people would
-interact with Joker.
-
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
-
-We recruited 5 participants with varying backgrounds. 3 participants
-were familiar with spreadsheet formulas. 3 participants had extensive
-web development experience, 1 had a small amount of prior web
-development experience, and 1 had no web development experience. 3
-participants had previously extracted data from websites.
-
-\hypertarget{protocol}{%
-\subsubsection{Protocol}\label{protocol}}
-
-The participants completed 7 web customization tasks across 2 websites.
-All participants attempted all the tasks.
-
-First, we asked participants to customize a website with a relatively
-simple HTML structure: the MIT EECS course catalog website. All data
-\emph{extraction} on this site can be performed with demonstrations
-alone in Joker, although augmentation still requires writing formulas.
-The specific tasks were the following: 1a) Extract course titles, 1b)
-Extract course prerequisites, 1c) Add a column that indicates whether a
-course has a prerequisite \& 1d) Add a column that indicates whether a
-course has no prerequisites and is offered in the fall term.
-
-Next, we asked participants to customize a website with a more complex
-HTML structure: the search results page for the eBay shopping website.
-Due to the website's complexity, demonstrations alone are not sufficient
-to extract data; users must also directly edit extraction formulas. The
-specific tasks were the following: 2a) Extract title from listings of
-Apple iPhones for sale, 2b) Extract the listing price for the phone, \&
-2c) Create a column that indicates whether a listing for a phone is
-sponsored.
-
-Each session was 60 minutes long and conducted over a recorded video
-conference. We started each session with a description of Joker and
-provided a brief tutorial of its main features on a sample website not
-used in the tasks. There was no time limit for completing the tasks.
-Users were encouraged to speak aloud as they worked.
-
-Because some of the tasks build on results of previous tasks, we wanted
-to ensure all participants made enough progress to gather useful
-feedback. Therefore, whenever a participant got stuck for several
-minutes, we recorded why they were stuck and then offered hints on how
-to proceed (such as suggestions to read formula documentation or open
-the browser dev tools). While all participants were able to complete all
-tasks with hints, this obviously does not mean they could have completed
-the task unassisted. Our goal was not to simply measure whether users
-completed the task, but rather to gain qualitative insight into the
-barriers they faced.
-
-\hypertarget{results}{%
-\subsubsection{Results}\label{results}}
-
-\emph{Unified interaction model.} Most participants took advantage of
-the unified interaction model to interleave extraction and augmentation
-tasks, rather than performing all extraction up front. For example, on
-task 1, most participants extracted the prerequisites by demonstration,
-added one or more columns to the table to perform some string operations
-on the prerequisites, and then continued on to extract more information
-from the web page by demonstration. Furthermore, we hypothesize that in
-a less controlled setting, users would be even more likely to interleave
-extraction and augmentation, since the task may be less well defined at
-the beginning.
-
-One usability issue with the unified model was that participants
-sometimes got confused about how their demonstrations would affect the
-contents of the table. For example, multiple participants intended to
-add a new column by demonstrating an extraction, but instead
-accidentally overwrote the contents of an existing column. This poses a
-design challenge because the user's demonstrations occur in the website,
-so they cannot directly interact with the table while demonstrating;
-this suggests that the interface needs to do a better job indicating
-where the results of a demonstration will be inserted.
-
-\emph{Extracting simple data.} On the relatively simple MIT course
-catalog website, all participants were able to extract the relevant data
-from the page within seconds, simply performing demonstrations with a
-few clicks. This suggests that when Joker's generalization algorithm
-works well, it can be an effective tool for data extraction, even for
-users with limited programming experience. P1 said: \emph{``you could
-hover and {[}the data{]} was already selected\ldots that was very
-nice''}. P3, upon seeing the tutorial for extraction by demonstration,
-said \emph{``that's like black magic.''}
-
-\emph{Extracting complex data.} On the more complex eBay website where
-demonstration alone was not sufficient, results were more varied. P1,
-who had no prior web development experience, struggled to complete the
-task, saying that \emph{``looking at HTML is a bit much''}; this
-suggests that more work could be done to make the experience usable for
-novices. However, users with more web development experience were able
-to use the tool to perform complex extractions, such as directly writing
-CSS selectors into the formula bar. P2 and P3 both reported that Joker's
-live feedback loop was easier to use and faster than other approaches to
-web extraction; P3 noted that \emph{``{[}with any other approach{]}, it
-would have been slower to specify and slower to validate that I
-specified it correctly.''}
-
-It was challenging for some participants to switch between using the
-browser's developer tools and the Joker interface when doing complex
-extraction tasks. While we chose not to build HTML inspection into the
-Joker UI because the browser already provides a very rich set of tools,
-users sometimes were not able to tell how elements in the Joker table
-corresponded to elements in the browser's element inspector.
-
-\emph{Writing formulas.} In general, participants were able to learn the
-formula language by using an autocomplete dropdown with inline
-documentation, which we developed as part of the Joker extension. In
-some cases, participants were able to immediately construct correct
-formulas on the first try; in other cases it took several attempts and
-some hints from the moderator to try a relevant function. While better
-documentation and error messages could help improve the learnability of
-the formula language, we also did not find it surprising that
-participants required some time to learn a completely unfamiliar formula
-language.
-
-\hypertarget{cognitive-dimensions-analysis}{%
-\subsection{Cognitive Dimensions
-Analysis}\label{cognitive-dimensions-analysis}}
-
-We analyzed Joker using the Cognitive Dimensions of Notation
-\citep{blackwell2001}, a heuristic evaluation framework that has been
-used to evaluate programming languages and visual programming systems
-\citep{satyanarayan2014, satyanarayan2014a, ledo2018}. When contrasting
-our tool with other scraping and customization tools, we find
-particularly meaningful differences along several dimensions:
-
-\emph{Progressive evaluation.} In Joker, a user can see the intermediate
-results of their extraction and augmentation work at any point, and
-adjust their future actions accordingly. The table user interface makes
-it easy to inspect the intermediate results and notice surprises like
-missing values.
-
-In contrast, traditional extraction typically requires editing the code,
-manually re-running it, and inspecting the results in an unstructured
-textual format, making it harder to progressively evaluate the results.
-Also, many end-user extraction tools \citep{chasins2018, lin2009}
-require the user to demonstrate all the data extractions they want to
-perform before showing any information about how those demonstrations
-will generalize across multiple examples.\footnote{This is an instance
-  where Joker's limitation of only scraping a single page at a time
-  proves beneficial. All the relevant data is already available on the
-  page without further network requests, making it possible to support
-  progressive evaluation with low latency. Other tools that support
-  scraping across multiple pages necessarily require a slower feedback
-  loop.}
-
-\emph{Premature commitment.} Many scraping tools require making a
-\emph{premature commitment} to a data schema: first, the user extracts a
-dataset, and then they perform augmentations using that data. Wildcard
-suffered from this problem: when writing code for extraction, a user
-would need to anticipate all future augmentations and extract the
-necessary data.
-
-Joker instead supports extracting data \emph{on demand}. The user can
-decide on their desired augmentations and extract data as needed to
-fulfill those tasks. There is never a need to eagerly guess what data
-will be needed in advance.
-
-We have also borrowed a technique from spreadsheets for avoiding
-premature commitment: default naming. New data columns are automatically
-assigned a single-letter name, so that the user does not need to
-prematurely think of a name before extracting the data. We have not yet
-implemented the capability to optionally rename demonstrated columns,
-but it would be straightforward to do so, and would provide a way to
-offer the benefits of names without requiring a premature commitment.
-
-\emph{Provisionality.} Joker makes it easy to try out an extraction
-action without fully committing to it. When the user hovers over any
-element in a website, they see a preview of how that data would be
-extracted into the table, and then they can click if they'd like to
-proceed. This makes it feel very fast and lightweight to try scraping
-different elements on the page.
-
-\emph{Viscosity.} Some scraping tools have high viscosity: they make it
-difficult to change a single part of an extraction specification without
-modifying the global structure. For example, in Rousillon
-\citep{chasins2018}, changing the desired demonstration for a single
-column of a table requires re-demonstrating all of the columns. In
-contrast, Joker allows a user to change the specification for a single
-column of a table without modifying the others, resulting in a lower
-viscosity in response to changes.
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Website}              & \textbf{Example Customization Achieved by Joker}                                        \\ \hline
+eBay, Amazon            & Filter listings by whether they have a "Sponsored" label.                        \\
+Amazon, Target & Sort search results by price and rating.                                                \\
+Google Scholar                & Filter publications for those whose title contains a user-provided keyword. \\
+Reddit, CNN, ABC  & Sort by the read times of articles. Filter already-visited articles.         \\
+Weather.com                   & Filter hourly weather to find sunny times of day.                                        \\
+Github                        & Sort a user's code repositories by stars to find popular work.                          \\
+Postmates, Uber Eats    & Sort restaurants by delivery time and delivery fee.                                     \\ \hline
+\end{tabular}
+\vspace{8pt}
+\caption{Examples of websites that Joker can be used to customize, including extraction and augmentation}
+\end{table*}
 
@@
 \section{Related Work}\label{sec:related-work}}
-
-Joker builds on existing work in end-user web customization, end-user
-web scraping and program synthesis.
 
@@
 beginning of the process and displaying an editable synthesized program.
-We hypothesize that focusing on a tight feedback loop rather than
-automation may support a scraping process that offers more expressive
-power and extends to a greater variety of websites, but further user
-testing is required to validate this hypothesis. Of course, better
-heuristics could benefit our model as well; the ideal system would make
-good guesses while giving the user full understanding and control of the
-extraction process.
 
@@
 program synthesis \citep{peleg2018}: the set of synthesized programs for
-a demonstration can be very large. The Program Navigation UI displays a
-natural language description of a space of possible programs, and lets
-the user choose different alternatives for parts of the generated
-expression. Joker shares the general idea of displaying synthesized
-programs, but only presents the top-ranked program; our tool might be
-improved by showing more candidate programs.
+a demonstration can be very large. Joker shares the general idea of
+displaying synthesized programs, but only presents the top-ranked
+program.
 
@@
 Chugh's notion of \emph{prodirect manipulation} \citep{chugh2016a},
-which aims to bridge the divide between programmatic and direct
-manipulation. The Sketch-N-Sketch system \citep{chugh2016} provides
-prodirect manipulation by allowing users to create an SVG shape via
-traditional programming and then switch to modifying its size or shape
-via direct manipulation.
+implemented in Sketch-N-Sketch \citep{chugh2016}, which aims to bridge
+the divide between programmatic and direct manipulation.
 
@@
 programming-by-demonstration (PBD) interface that makes it easy for
-end-users to program to create formulas. This unified interaction model
-allows end-users to move seamlessly between extraction and augmentation,
-resulting in a more iterative and free-form workflow for web
-customization.
+end-users to program to create formulas. The main area of future work
+involves making the formula language more accessible to end-users not
+familiar with CSS selectors. Our ultimate goal is to enable anyone that
+uses the web to customize websites in the course of their daily use in
+an intuitive and flexible way.
 
-The main area of future work involves making the formula language more
-accessible to end-users not familiar with CSS selectors. FlashProg
-offers some clues through its use of natural language descriptions to
-explain synthesized extraction programs. One avenue for explaining CSS
-selectors could be by extracting semantic web content associated with
-the elements they select, as seen in systems like Thresher
-\citep{hogue2005}.
+% \printbibliography
 
-Our ultimate goal is to enable anyone that uses the web to customize
-websites in the course of their daily use in an intuitive and flexible
-way. This will in turn make the malleability of the web a reality for
-all of its users.
-
-\newpage
-
-\bibliographystyle{IEEEtran}
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{references-bibtex.bib}
@@
 \end{document}
+\endinput
+%%
+%% End of file `sample-sigconf.tex'.

### 2021-08-02 compile-latex-acm.sh

@@ -1,19 +1,0 @@
-set -e
-
-pandoc \
-  --filter conditional-render \
-  --filter pandoc-crossref \
-  --citeproc \
-  --bibliography=references-bibtex.bib\
-  -s \
-  -o \
-  paper-acm.tex \
-  --template=templates/sigconf.pandoc \
-  --natbib \
-  --metadata=format:pdf \
-  paper.md
-
-pdflatex paper-acm.tex
-bibtex paper-acm
-pdflatex -interaction=batchmode paper-acm.tex
-pdflatex -interaction=batchmode paper-acm.tex

### 2021-08-02 compile-latex.sh

@@ -3,11 +3,13 @@ set -e
 pandoc \
   --filter conditional-render \
   --filter pandoc-crossref \
+  --citeproc \
+  --bibliography=references-bibtex.bib\
   -s \
   -o \
   paper.tex \
+  --template=templates/sigconf.pandoc \
   --natbib \
-  --template=ieee.pandoc \
   --metadata=format:pdf \
   paper.md
 
@@ -15,4 +17,3 @@ pdflatex paper.tex
 bibtex paper
 pdflatex -interaction=batchmode paper.tex
 pdflatex -interaction=batchmode paper.tex
-cp paper.pdf index.pdf

### 2021-08-04 paper.tex
Trim example scenario, move implementation to appendix and add demo video

@@
 
+\begin{figure*}
+  \includegraphics[width=\textwidth]{media/ebay.png}
+  \caption{\label{fig:ebay}Scraping and customizing eBay by unified demonstration and formulas.}
+\end{figure*}
+
 \textbf{A PBD interface for creating extraction formulas}: Directly
@@
 Joker enables a user to complete a useful customization task. In
-Section~\ref{sec:implementation}, we outline the implementation of our
-formula language and user interface, as well as the algorithms used by
-our PBD interface. We evaluate our approach in
-Section~\ref{sec:evaluation} by describing a suite of case studies in
-which we used Joker to extract and augment a variety of websites in
-order to characterize its capabilities and limitations. Joker relates to
-existing work not only in end-user web customization, but also in
-end-user web scraping and program synthesis, which we discuss in
-Section~\ref{sec:related-work}. Finally, we discuss opportunities for
-future work in Section~\ref{sec:conclusion}.
+Section~\ref{sec:implementation}, we briefly describe the implementation
+of our formula language and user interface, as well as the algorithms
+used by our PBD interface.
+
+We have performed two evaluations of our approach, presented in
+Section~\ref{sec:evaluation}. First, we describe a suite of case studies
+in which we used Joker to extract and augment a variety of websites in
+order to characterize its capabilities and limitations. Second, we
+describe a formative user study with five participants, which showed
+that users were generally able to use Joker to perform useful extraction
+and augmentation tasks, but which also uncovered limitations,
+particularly for less experienced users trying to extract data from more
+complex websites.
+
+Joker relates to existing work not only in end-user web customization,
+but also in end-user web scraping and program synthesis, which we
+discuss in Section~\ref{sec:related-work}. Finally, we discuss
+opportunities for future work in Section~\ref{sec:conclusion}.
 
@@
 
-Here is an example scenario, illustrated in Figure~\ref{fig:ebay}, and
-demonstrated in the video accompanying this paper. Jen is searching for
-a karaoke machine on eBay, a shopping website. She wants to use Joker to
-sort products by price within a page of search results, a feature not
-supported by eBay.
-
-\begin{figure*}
-  \includegraphics[width=\textwidth]{media/ebay.png}
-  \caption{\label{fig:ebay}Scraping and customizing eBay by unified demonstration and formulas.}
-\end{figure*}
-
-\emph{Extracting Product Titles \& Prices By Demonstration}.
-(Figure~\ref{fig:ebay} Part A): Jen initiates Joker through the browser
-context menu. As she hovers over the product title, Joker provides two
-kinds of live feedback. First, it highlights the titles of all the
-corresponding product listings on the page, to indicate how it has
-generalized Jen's intent based on her demonstration of a single example
-product. Second, a column of the table is populated with the values that
-will be extracted, giving a preview of how the extracted data would
-look. To commit to this extraction, Jen clicks on the product title. She
-repeats a similar process to extract the price.
-
-When she clicks one of the cells in column \texttt{B}, the formula bar
-above the table displays the extraction formula that was generated from
-her demonstration:
-
-\texttt{=QuerySelector(rowElement,\ "span.s-item\_\_price")}
-
-This formula produces the values in column \texttt{B}. For each row in
-the table, Joker has a created a reference to the corresponding DOM
-element, accessible through the special identifier \texttt{rowElement}.
-The \texttt{QuerySelector} function runs the specified CSS selector
-(\texttt{span.s-item\_\_price}) within the row element to extract the
-price of each item. While Jen could directly edit this formula, in this
-case the values in the table are correct, so there's no need to edit the
-formula.
-
-\emph{Sorting Products By Price}. (Figure~\ref{fig:ebay} Part B): Next,
-Jen wants to sort the table by price, but she realizes that the column
-of prices is a list of strings containing the \texttt{\$} symbol. She
-needs to \emph{augment} this raw data by turning the strings into
-numbers. In the next column (\texttt{C}), Jen starts typing a formula,
-and uses an autocomplete dropdown to find a relevant function that
-extracts numeric values from strings:
-
-\texttt{=ExtractNumber(B)}
-
-Now column C contains numeric values, so Jen can sort the table by
-price. Because the table is synchronized with the website, the product
-listings become sorted as well.
-
-\emph{Extracting Product URL With Formulas} (Figure~\ref{fig:ebay} Part
-C): While completing the previous task, Jen realizes there is another
-customization she would find useful: prioritizing products for which she
-has not yet visited the details page for the listing. To do this, she
-must first return to \emph{extracting} more relevant data from the page.
-
-Each product listing links to a page for the specific product, but
-because the URL is not visible in the page, it's not possible to
-directly extract it by demonstration. However, Jen can still achieve the
-goal by directly writing an extraction formula.
-
-Jen has some basic knowledge of HTML, which she can leverage to write
-the formula. She opens the browser developer tools, and observes that
-the listing title is represented by a link tag with a heading inside:
-
-\begin{verbatim}
-<a href="LISTING PAGE URL">
-  <h3>LISTING NAME</h3>
-</a>
-\end{verbatim}
-
-Since there is already a column \texttt{A} in the table representing the
-product's title, she can use this as a starting point to write the
-formula:
-
-\texttt{=GetAttribute(GetParent(A),\ "href")}
-
-This formula first calls the \texttt{GetParent} function on column
-\texttt{A}, traversing up a level from the
-\texttt{\textless{}h3\textgreater{}} elements to the
-\texttt{\textless{}a\textgreater{}} elements. Then,
-\texttt{GetAttribute} extracts the \texttt{href} value containing the
-link URL. After running this formula, the table contains a column
-\texttt{D} with the URL for each product.
-
-\emph{Sorting Products By Whether They Have Been Visited}
-(Figure~\ref{fig:ebay} Part C): After performing that extraction, Jen
-can write a final augmentation formula to indicate whether she has
-visited the corresponding product page:
-
-\texttt{=Visited(D)}
-
-The \texttt{Visited} function checks whether a URL is present in the
-browser history and returns a boolean value represented by a checkbox.
-Jen can then sort by this column to put listings that she has not yet
-visited at the top of the page.
-
-Using Joker, Jen was able to not only achieve her initial customization
-goal to sort the products by price but also perform a customization she
-did not plan to do. This was made possible by Joker's unified
-interaction model for web customization which enabled her to interleave
-extraction and augmentation. While we have described only a single
-illustrative scenario in this example, Joker is flexible enough to
-support a wide range of other useful customizations and workflows on
-various websites, described in more detail in
-Section~\ref{sec:evaluation}.
+This section describes an example scenario, illustrated in
+Figure~\ref{fig:ebay}, and demonstrated in the video accompanying this
+paper. Jen is searching for a karaoke machine on eBay, a shopping
+website. She wants to use Joker to sort products by price within a page
+of search results, a feature not supported by eBay. Because Joker
+supports interleaving extraction and augmentation tasks on the fly, Jen
+is also able to extract the URLs of products to determine whether they
+have been visited and use that to further sort the products. While we
+have described only a single illustrative scenario in this example,
+Joker is flexible enough to support a wide range of other useful
+customizations and workflows on various websites, described in more
+detail in Section~\ref{sec:evaluation}.
 
@@
 
-In this section, we describe Joker's formula language in more detail.
-Then, we briefly outline the \emph{wrapper induction}
-\citep{kushmerick2000} algorithm that Joker's PBD interface uses to
-synthesize the row element and column selectors presented in formulas.
+In this section, we briefly describe Joker's formula language and the
+\emph{wrapper induction} \citep{kushmerick2000} algorithm that Joker's
+PBD interface uses to synthesize the row element and column selectors
+presented in formulas. Figure~\ref{fig:overview} illustrates the entire
+process.
 
@@
 Joker extends this base language with new constructs which enable it to
-apply to \emph{data extraction} instead of just augmentation.
-
-We added DOM elements as a data type in the language, alongside strings,
-numbers, and booleans. Because the language runs in a JavaScript
-interpreter, we simply use native JavaScript values to represent DOM
-elements in the language. DOM elements are displayed visually by showing
-their inner text contents. They can also be implicitly typecast to
-strings for use in other formulas; for example, a string manipulation
-formula like \texttt{Substring} can be called on a DOM element value,
-and will operate on its text contents.
-
-We also added several functions to the formula language for traversing
-the DOM and performing extractions, summarized below with their types:
-
-\begin{itemize}
-\tightlist
-\item
-  \texttt{QuerySelector(el:\ Element,\ sel:\ string):\ Element}.
-  Executes the CSS selector \texttt{sel} inside of element \texttt{el},
-  and returns the first matching element.
-\item
-  \texttt{GetAttribute(el:\ Element,\ attribute:\ string):\ string}.
-  Returns the value for an attribute on an element.
-\item
-  \texttt{GetParent(el:\ Element):\ Element}. Returns the parent of a
-  given element.
-\end{itemize}
-
-To extract data from a row, formulas need a way to reference the current
-row, so we added a construct to support this use case. Every row in the
-table maps to one DOM element in the page; we allow formulas to access
-this DOM element via a special keyword, \texttt{rowElement}. In some
-sense, \texttt{rowElement} can be seen as a hidden extra column of data
-in the table containing DOM elements.
-
-While many more functions could be added to expose more of the
-underlying DOM API, we found that in practice these three functions
-provided ample power through composition. For example, in
-Section~\ref{sec:examples} we showed how \texttt{GetParent} and
-\texttt{GetAttribute} can be composed to traverse the DOM and extract
-the URL associated with a product listing.
+apply to \emph{data extraction} instead of just augmentation. More
+information can be found in Appendix A.
 
@@
 implemented a set of heuristics inspired by Vegemite \citep{lin2009} for
-wrapper induction, illustrated in Figure~\ref{fig:overview}.
+wrapper induction, outlined in Appendix B.
 
@@
 
-We evaluate our interaction model and tool by describing the results of
-our use of Joker to extract data and perform customizations on popular
-websites. For the websites on which Joker can be used, we provide the
-sequence of interactions needed to achieve the customizations; for the
-websites on which Joker fails, we explain the relevant limitations.
+We evaluate our interaction model and tool in terms of two research
+questions:
+
+\emph{RQ1: What kinds of websites can this model operate effectively
+on?} We evaluate this with a suite of case studies that demonstrate its
+capabilities and limitations.
+
+\emph{RQ2: How are users of different backgrounds able to use the
+system?} We evaluate this with a small formative user study.
+
+\hypertarget{case-studies}{%
+\subsection{Case Studies}\label{case-studies}}
+
+Our first evaluation describes the results of our use of Joker to
+extract data and perform customizations on popular websites.
 
 \hypertarget{successful-applications}{%
-\subsection{Successful Applications}\label{successful-applications}}
+\subsubsection{Successful Applications}\label{successful-applications}}
 
 We have used Joker to achieve a variety of customizations across many
-websites. Table 1 summarizes examples we have found on popular websites.
+websites.
 
@@
 \hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
+\subsubsection{Limitations}\label{limitations}}
 
@@
 
-\begin{table*}[]
-\centering
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Website}              & \textbf{Example Customization Achieved by Joker}                                        \\ \hline
-eBay, Amazon            & Filter listings by whether they have a "Sponsored" label.                        \\
-Amazon, Target & Sort search results by price and rating.                                                \\
-Google Scholar                & Filter publications for those whose title contains a user-provided keyword. \\
-Reddit, CNN, ABC  & Sort by the read times of articles. Filter already-visited articles.         \\
-Weather.com                   & Filter hourly weather to find sunny times of day.                                        \\
-Github                        & Sort a user's code repositories by stars to find popular work.                          \\
-Postmates, Uber Eats    & Sort restaurants by delivery time and delivery fee.                                     \\ \hline
-\end{tabular}
-\vspace{8pt}
-\caption{Examples of websites that Joker can be used to customize, including extraction and augmentation}
-\end{table*}
+\hypertarget{user-study}{%
+\subsection{User Study}\label{user-study}}
+
+Our second evaluation reports a small, formative user study we conducted
+to understand how users would interact with Joker.
+
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
+
+We recruited 5 participants with varying backgrounds. 3 participants
+were familiar with spreadsheet formulas. 3 participants had extensive
+web development experience, 1 had a small amount of prior web
+development experience, and 1 had no web development experience. 3
+participants had previously extracted data from websites.
+
+\hypertarget{protocol}{%
+\subsubsection{Protocol}\label{protocol}}
+
+The participants completed 7 web customization tasks across 2 websites.
+All participants attempted all the tasks.
+
+First, we asked participants to customize a website with a relatively
+simple HTML structure: the MIT EECS course catalog website. All data
+\emph{extraction} on this site can be performed with demonstrations
+alone in Joker, although augmentation still requires writing formulas.
+The specific tasks were the following: 1a) Extract course titles, 1b)
+Extract course prerequisites, 1c) Add a column that indicates whether a
+course has a prerequisite \& 1d) Add a column that indicates whether a
+course has no prerequisites and is offered in the fall term.
+
+Next, we asked participants to customize a website with a more complex
+HTML structure: the search results page for the eBay shopping website.
+Due to the website's complexity, demonstrations alone are not sufficient
+to extract data; users must also directly edit extraction formulas. The
+specific tasks were the following: 2a) Extract title from listings of
+Apple iPhones for sale, 2b) Extract the listing price for the phone, \&
+2c) Create a column that indicates whether a listing for a phone is
+sponsored.
+
+Each session was 60 minutes long and conducted over a recorded video
+conference. We started each session with a description of Joker and
+provided a brief tutorial of its main features on a sample website not
+used in the tasks. There was no time limit for completing the tasks.
+Users were encouraged to speak aloud as they worked.
+
+Because some of the tasks build on results of previous tasks, we wanted
+to ensure all participants made enough progress to gather useful
+feedback. Therefore, whenever a participant got stuck for several
+minutes, we recorded why they were stuck and then offered hints on how
+to proceed (such as suggestions to read formula documentation or open
+the browser dev tools). While all participants were able to complete all
+tasks with hints, this obviously does not mean they could have completed
+the task unassisted. Our goal was not to simply measure whether users
+completed the task, but rather to gain qualitative insight into the
+barriers they faced.
+
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
+
+We have categorized our results into the following four groups:
+
+\emph{Unified interaction model.} Most participants took advantage of
+the unified interaction model to interleave extraction and augmentation
+tasks, rather than performing all extraction up front. For example, on
+task 1, most participants extracted the prerequisites by demonstration,
+added one or more columns to the table to perform some string operations
+on the prerequisites, and then continued on to extract more information
+from the web page by demonstration. Furthermore, we hypothesize that in
+a less controlled setting, users would be even more likely to interleave
+extraction and augmentation, since the task may be less well defined at
+the beginning.
+
+One usability issue with the unified model was that participants
+sometimes got confused about how their demonstrations would affect the
+contents of the table. For example, multiple participants intended to
+add a new column by demonstrating an extraction, but instead
+accidentally overwrote the contents of an existing column. This poses a
+design challenge because the user's demonstrations occur in the website,
+so they cannot directly interact with the table while demonstrating;
+this suggests that the interface needs to do a better job indicating
+where the results of a demonstration will be inserted.
+
+\emph{Extracting simple data.} On the relatively simple MIT course
+catalog website, all participants were able to extract the relevant data
+from the page within seconds, simply performing demonstrations with a
+few clicks. This suggests that when Joker's generalization algorithm
+works well, it can be an effective tool for data extraction, even for
+users with limited programming experience. P1 said: \emph{``you could
+hover and {[}the data{]} was already selected\ldots that was very
+nice''}. P3, upon seeing the tutorial for extraction by demonstration,
+said \emph{``that's like black magic.''}
+
+\emph{Extracting complex data.} On the more complex eBay website where
+demonstration alone was not sufficient, results were more varied. P1,
+who had no prior web development experience, struggled to complete the
+task, saying that \emph{``looking at HTML is a bit much''}; this
+suggests that more work could be done to make the experience usable for
+novices. However, users with more web development experience were able
+to use the tool to perform complex extractions, such as directly writing
+CSS selectors into the formula bar. P2 and P3 both reported that Joker's
+live feedback loop was easier to use and faster than other approaches to
+web extraction; P3 noted that \emph{``{[}with any other approach{]}, it
+would have been slower to specify and slower to validate that I
+specified it correctly.''}
+
+It was challenging for some participants to switch between using the
+browser's developer tools and the Joker interface when doing complex
+extraction tasks. While we chose not to build HTML inspection into the
+Joker UI because the browser already provides a very rich set of tools,
+users sometimes were not able to tell how elements in the Joker table
+corresponded to elements in the browser's element inspector.
+
+\emph{Writing formulas.} In general, participants were able to learn the
+formula language by using an autocomplete dropdown with inline
+documentation, which we developed as part of the Joker extension. In
+some cases, participants were able to immediately construct correct
+formulas on the first try; in other cases it took several attempts and
+some hints from the moderator to try a relevant function. While better
+documentation and error messages could help improve the learnability of
+the formula language, we also did not find it surprising that
+participants required some time to learn a completely unfamiliar formula
+language.
 
@@
 displaying synthesized programs, but only presents the top-ranked
-program.
-
-More broadly, Joker's use of PBD to generate editable code embodies Ravi
-Chugh's notion of \emph{prodirect manipulation} \citep{chugh2016a},
-implemented in Sketch-N-Sketch \citep{chugh2016}, which aims to bridge
-the divide between programmatic and direct manipulation.
+program. More broadly, Joker's use of PBD to generate editable code
+embodies Ravi Chugh's notion of \emph{prodirect manipulation}
+\citep{chugh2016a}, implemented in Sketch-N-Sketch \citep{chugh2016},
+which aims to bridge the divide between programmatic and direct
+manipulation.
 
@@
 
+\newpage
+
 % \printbibliography
@@
 
+\clearpage
+\hypertarget{appendix}{%
+\section*{Appendix}\label{appendix}}
+
+\hypertarget{appendix-a}{%
+\subsection*{A: Extraction Formulas}\label{appendix-a}}
+
+Joker adds DOM elements as a data type to Wildcard's formula language, alongside strings,
+numbers, and booleans. Because the language runs in a JavaScript
+interpreter, we simply use native JavaScript values to represent DOM
+elements in the language. DOM elements are displayed visually by showing
+their inner text contents. They can also be implicitly typecast to
+strings for use in other formulas; for example, a string manipulation
+formula like \texttt{Substring} can be called on a DOM element value,
+and will operate on its text contents.
+
+We also added several functions to the formula language for traversing
+the DOM and performing extractions, summarized below with their types:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{QuerySelector(el:\ Element,\ sel:\ string):\ Element}.
+  Executes the CSS selector \texttt{sel} inside of element \texttt{el},
+  and returns the first matching element.
+\item
+  \texttt{GetAttribute(el:\ Element,\ attribute:\ string):\ string}.
+  Returns the value for an attribute on an element.
+\item
+  \texttt{GetParent(el:\ Element):\ Element}. Returns the parent of a
+  given element.
+\end{itemize}
+
+To extract data from a row, formulas need a way to reference the current
+row, so we added a construct to support this use case. Every row in the
+table maps to one DOM element in the page; we allow formulas to access
+this DOM element via a special keyword, \texttt{rowElement}. In some
+sense, \texttt{rowElement} can be seen as a hidden extra column of data
+in the table containing DOM elements.
+
+While many more functions could be added to expose more of the
+underlying DOM API, we found that in practice these three functions
+provided ample power through composition. For example, in
+Section~\ref{sec:examples} we showed how \texttt{GetParent} and
+\texttt{GetAttribute} can be composed to traverse the DOM and extract
+the URL associated with a product listing.
+
+\hypertarget{appendix-b}{%
+\subsection*{B: Wrapper Induction Algorithm}\label{appendix-b}}
+
+Our wrapper induction algorithm implements a set of heuristics inspired by Vegemite
+as described below:
+
+\hypertarget{determining-row-elements}{%
+\subsubsection*{Determining Row
+Elements}\label{determining-row-elements}}
+
+The user starts by demonstrating an element \(v\), representing a value
+that should be in the table. From that demonstration, we must find a set
+of \emph{row elements} that represent the rows of the table. We could
+naively assume that \(parent(v)\) is the row containing \(v\), but often
+\(v\) is deeply nested inside its containing row; we must determine
+which ancestor of \(v\) is likely to be the row.
+
+Intuitively, we solve this problem by assuming that all rows share some
+similar internal structure. In particular, we expect most rows to
+contain a value for the demonstrated column. (If there were no missing
+data, we'd expect \emph{all} rows to contain data for this column.)
+
+Formally: assume a function \(select(el, s)\) which runs a CSS selector
+that returns the set of elements matching \(s\) within \(el\). We
+generate a set of plausible candidates \(P\), consisting of pairs of a
+row element and a CSS selector:
+
+\(P = \{ (r, s) \mid r \in ancestors(v) \land select(r, s) = \{v\} \}\)
+
+For each candidate \((r, s) \in P\), we compute a weight function \(w\),
+which is based on the number of siblings of \(r\) that have ``similar
+structure'', defined by checking whether running \(s\) within the
+sibling also returns a unique element.
+
+\(w(r, s) = |\{ r' \mid r' \in siblings(r) \land |select(r', s) | = 1 \}|\)
+
+We then choose the candidate with the highest weight. In case of ties,
+the candidate closer to \(v\) in the tree (i.e., lower in the tree)
+wins. Given a winning candidate \((r, s)\), the full set of row elements
+is \(\{r\} \cup siblings(r)\).
+
+\hypertarget{synthesizing-css-selectors-for-column-values}{%
+\subsubsection*{Synthesizing CSS Selectors For Column
+Values}\label{synthesizing-css-selectors-for-column-values}}
+
+Once we have determined the row elements, next we must choose a CSS
+selector that will be used to identify the demonstrated value within its
+row.
+
+Given a demonstrated value \(v\) within a row element \(r\), we generate
+two kinds of plausible selectors:
+
+\begin{itemize}
+\tightlist
+\item
+  selectors using CSS classes, which are manual annotations on DOM
+  elements added by the website's programmers, typically for styling
+  purposes (e.g.~"item\_\_price")
+\item
+  selectors using positional indexes within the tree, using the
+  \texttt{nth-child} CSS selector (e.g.~\texttt{nth-child(2)},
+  representing the second child of an element)
+\end{itemize}
+
+The minimum criteria for a plausible selector \(s\) is that it uniquely
+identifies the value within the row: \(select(r, s) = \{v\}\). But there
+may be many plausible selectors, so we must pick a best one.
+
+We first prioritize selectors using classes, because they tend to be
+more robust to changes on the website. A single selector can combine
+multiple classes, but we prefer using fewer classes when possible. If no
+plausible class-based selector can be generated (for example, if the
+relevant elements don't have any classes to query), we fall back to
+using a positional index selector. This kind of selector can always be
+generated regardless of the contents of the page, but tends to be less
+accurate and robust.
+
 \end{document}

### 2021-08-04 compile-latex.sh

@@ -17,3 +17,4 @@ pdflatex paper.tex
 bibtex paper
 pdflatex -interaction=batchmode paper.tex
 pdflatex -interaction=batchmode paper.tex
+cp paper.pdf index.pdf

### 2021-08-05 paper.tex
Put back abstract, remove sigconf template reference and persmissions section and trim user study

@@
 \settopmatter{printfolios=true}
+\settopmatter{printacmref=false}
+\renewcommand\footnotetextcopyrightpermission[1]{}
+\pagestyle{plain}
 
@@
 %% article.
-%% \begin{abstract}
-%%  
-%% \end{abstract}
+ \begin{abstract}
+  Tools that enable end-users to customize websites typically use a
+  two-stage workflow: first, users extract data into a structured form;
+  second, they use that extracted data to augment the original website
+  in some way. This two-stage workflow poses a usability barrier because
+  it requires users to make upfront decisions about what data to
+  extract, rather than allowing them to incrementally extract data as
+  they augment it.
+
+  In this paper, we present a new, unified interaction model for web
+  customization that encompasses both extraction and augmentation. The
+  key idea is to provide users with a spreadsheet-like formula language
+  that can be used for both data extraction and augmentation. We also
+  provide a programming-by-demonstration (PBD) interface that allows
+  users to create data extraction formulas by clicking on elements in
+  the website. This model allows users to naturally and iteratively move
+  between extraction and augmentation.
+
+  To illustrate our unified interaction model, we have implemented a
+  tool called Joker which is an extension of Wildcard, a prior web
+  customization system. Through case studies, we show that Joker can be
+  used to customize many real-world websites. We also present a
+  formative user study with five participants, which showed that people
+  with a wide range of technical backgrounds can use Joker to customize
+  websites, and also revealed some interesting limitations of our
+  approach. Finally, we present a heuristic evaluation of our design
+  using the Cognitive Dimensions framework.
+ \end{abstract}
 
@@
 
-Each session was 60 minutes long and conducted over a recorded video
-conference. We started each session with a description of Joker and
-provided a brief tutorial of its main features on a sample website not
-used in the tasks. There was no time limit for completing the tasks.
-Users were encouraged to speak aloud as they worked.
-
 Because some of the tasks build on results of previous tasks, we wanted

### 2021-08-05 paper.tex
Fix typo in conclusion

@@
 programming-by-demonstration (PBD) interface that makes it easy for
-end-users to program to create formulas. The main area of future work
-involves making the formula language more accessible to end-users not
-familiar with CSS selectors. Our ultimate goal is to enable anyone that
-uses the web to customize websites in the course of their daily use in
-an intuitive and flexible way.
+end-users to create formulas. The main area of future work involves
+testing with more users and making the formula language more accessible
+to end-users not familiar with CSS selectors. Our ultimate goal is to
+enable anyone that uses the web to customize websites in the course of
+their daily use in an intuitive and flexible way.
 

### 2021-08-05 paper.tex
Remove page header boilerplate
Remove reference to cognitive dimensions in abstract

@@
 \renewcommand\footnotetextcopyrightpermission[1]{}
-\pagestyle{plain}
 
@@
   websites, and also revealed some interesting limitations of our
-  approach. Finally, we present a heuristic evaluation of our design
-  using the Cognitive Dimensions framework.
+  approach.
  \end{abstract}
@@
 \maketitle
+\pagestyle{plain}
 
@@
 
-Our wrapper induction algorithm implements a set of heuristics inspired by Vegemite
+Joker's wrapper induction algorithm implements a set of heuristics inspired by Vegemite
 as described below:
